---
title: "Revised dataset - Cluster profiler"
output: html_document
date: "2023-08-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load libraries}
library(clusterProfiler)
library(dplyr)
library(ggplot2)
library(reshape2)
library(treemapify)
library(Seurat)
library(tidyverse)
library(viridis)
library(org.Hs.eg.db)
```

```{r set seed and project name, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r load seurat object}
harmonized.seurat <- readRDS('./revisedDataset/rds/FLCvNML_Named-obj.rds')
```

## Cluster Profiler by cell type and not status

```{r Load markers csv}
dir.create("./revisedDataset/clusterProfiler")
markers <- read.csv("./revisedDataset/cell_type_assignment/FLCvNML_HighlyEnrichedMarkers_CLUSTERNAMED_logFC.25_wilcox.csv") %>% 
  filter(avg_log2FC >= 1.0)
```

```{r Add EntrezID to markers dataframe}
geneid <- markers$gene
markers$entrezid <- AnnotationDbi::select(org.Hs.eg.db,
                                          keys = geneid, 
                                          columns = "ENTREZID", 
                                          keytype = "SYMBOL")
```

```{r Generate clusterlist of Entrez ID for each cell type}
cluster_names <- levels(harmonized.seurat)
clusterprofilerlist <- list()

for (cluster_name in cluster_names) {
  # Subset the genes based on the current cluster
  cluster_genes <- subset(markers$entrezid$ENTREZID, markers$cluster == cluster_name)[1:100]
  
  # Store the subset of genes in the list using the cluster name as the key
  clusterprofilerlist[[cluster_name]] <- cluster_genes
}
```

```{r GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist,
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_log2FC1.0.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_log2FC1.0.csv")
```

```{r GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_GOSimplified_log2FC1.0.png", width = 11, height = 11, units = "in")
```

```{r PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist,
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 3) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_log2FC1.0.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_log2FC1.0.csv")
```

## Cluster profiler by cell type and status

```{r Load markers}
markers <- read.csv("./revisedDataset/FLCvNML_DEG_clusterNamed_FLCvsNML-MAST.csv") %>% 
  filter(avg_log2FC >= 0.5 | avg_log2FC <= -0.5, p_val_adj <= 0.05)
```

```{r Generate EntrezID in markers dataframe}
geneid <- markers$gene
markers$entrezid <- AnnotationDbi::select(org.Hs.eg.db,
                                          keys = geneid, 
                                          columns = "ENTREZID", 
                                          keytype = "SYMBOL")
```

```{r Generate cluster list by celltype and status}
cluster_names <- levels(harmonized.seurat)
clusterprofilerlist <- list()

# Loop over each cluster name
for (cluster_name in cluster_names) {
  # Subset the genes based on the current cluster for FLC (avg_log2FC >= 0.5)
  cluster_genes_flc <- subset(markers$entrezid$ENTREZID, markers$cluster == cluster_name & markers$avg_log2FC >= 0.5)[1:100]
  
  # Store the subset of genes in the list using the cluster name as the key with the addition of "-FLC"
  clusterprofilerlist[[paste0(cluster_name, "-FLC")]] <- cluster_genes_flc

  # Subset the genes based on the current cluster for NML (avg_log2FC <= -0.5)
  cluster_genes_nml <- subset(markers$entrezid$ENTREZID, markers$cluster == cluster_name & markers$avg_log2FC <= -0.5)[1:100]

  # Store the subset of genes in the list using the cluster name as the key with the addition of "-NML"
  clusterprofilerlist[[paste0(cluster_name, "-NML")]] <- cluster_genes_nml
}
```

```{r Complete case}
# Create an empty list to store the results
clusterprofilerlist <- list()

# Loop over each cluster name
for (cluster_name in cluster_names) {
  # Subset the genes based on the current cluster for FLC (avg_log2FC >= 0.5) and skip "NA" entries
  cluster_genes_flc <- subset(markers$entrezid$ENTREZID, 
                              markers$cluster == cluster_name & 
                              markers$avg_log2FC >= 0.5 & 
                              complete.cases(markers$entrezid$ENTREZID))[1:100]
  
  # Store the subset of genes in the list using the cluster name as the key with the addition of "-FLC"
  clusterprofilerlist[[paste0(cluster_name, "-FLC")]] <- cluster_genes_flc

  # Subset the genes based on the current cluster for NML (avg_log2FC <= -0.5) and skip "NA" entries
  cluster_genes_nml <- subset(markers$entrezid$ENTREZID, 
                              markers$cluster == cluster_name & 
                              markers$avg_log2FC <= -0.5 & 
                              complete.cases(markers$entrezid$ENTREZID))[1:100]

  # Store the subset of genes in the list using the cluster name as the key with the addition of "-NML"
  clusterprofilerlist[[paste0(cluster_name, "-NML")]] <- cluster_genes_nml
}

```

### Epithelial 1 cluster comparison

```{r Epi 1 - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[1:2],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Epi1_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Epi1_log2FC0.5-completeCase.csv")
```

```{r Epi 1 - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Epi1_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Epi 1 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[1:2],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi1_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi1_log2FC0.5-completeCase.csv")
```


### Epithelial 2 cluster comparison

```{r Epi 2 - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[3:4],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Epi2_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Epi2_log2FC0.5-completeCase.csv")
```

```{r Epi 2 - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Epi2_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Epi 2 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[3:4],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi2-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi2_log2FC0.5-completeCase.csv")
```


### Endothelial cluster comparison

```{r Endo - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[5:6],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Endo_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Endo_log2FC0.5-completeCase.csv")
```

```{r Endo - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Endo_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Endo - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[5:6],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Endo-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Endo_log2FC0.5-completeCase.csv")
```

### Epithelial 3 cluster comparison

```{r Epi 3 - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[7:8],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Epi3_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Epi3_log2FC0.5-completeCase.csv")
```

```{r Epi 3 - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Epi3_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Epi 3 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[7:8],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi3-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi3_log2FC0.5-completeCase.csv")
```

### Epithelial 4 cluster comparison

```{r Epi 4 - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[9:10],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Epi4_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Epi4_log2FC0.5-completeCase.csv")
```

```{r Epi 4 - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Epi4_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Epi 4 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[9:10],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi4-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Epi4_log2FC0.5-completeCase.csv")
```

### Stellate cluster comparison

```{r Stellate - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[11:12],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Stellate_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Stellate_log2FC0.5-completeCase.csv")
```

```{r Stellate - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Stellate_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Stellate - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[11:12],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Stellate-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Stellate_log2FC0.5-completeCase.csv")
```





### Lymphocyte 1 cluster comparison

```{r Lymphocyte 1 - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[13:14],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Lymp1_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Lymp1_log2FC0.5-completeCase.csv")
```

```{r Lymphocyte 1 - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Lymp1_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Lymphocyte 1 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[13:14],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Lymp1-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Lymph1_log2FC0.5-completeCase.csv")
```


### Cholangiocyte cluster comparison

```{r Cholangiocyte - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[15:16],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Cholangio_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Cholangio_log2FC0.5-completeCase.csv")
```

```{r Cholangiocyte - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Cholangio_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Cholangiocyte - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[15:16],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Cholangio-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Cholangio_log2FC0.5-completeCase.csv")
```





### Macrophage cluster comparison

```{r Macrophages - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[17:18],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Macropahes_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Macrophages_log2FC0.5-completeCase.csv")
```

```{r Macrophages - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Macrophages_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Macrophages - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[17:18],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Macropahes-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Macrophages_log2FC0.5-completeCase.csv")
```







### Lymphocyte 2 cluster comparison

```{r Lymphocyte 2 - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[19:20],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Lymph2_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Lymph2_log2FC0.5-completeCase.csv")
```

```{r Lymphocyte 2 - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Lymph2_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Lymphocyte 2 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[19:20],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Lymph2-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Lymph1_log2FC0.5-completeCase.csv")
```






### Epithelial-like cluster comparison

```{r Epithelial-like - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[21:22],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_EpiLike_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_EpiLike_log2FC0.5-completeCase.csv")
```

```{r Epithelial like - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_EpiLike_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Lymphocyte 2 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[21:22],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_EpiLike-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_EpiLike_log2FC0.5-completeCase.csv")
```






### Epithelial-like cluster comparison

```{r Erythroid - GO}
cc.go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[23:24],
                                         fun = "enrichGO", 
                                         OrgDb= org.Hs.eg.db, 
                                         ont= "BP",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc.go, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 

ggsave("./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_Ery_GO_log2FC0.5-completeCase.png", width = 11, height = 30, units = "in")

write.csv(cc.go@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_clusterCompare_GO_Ery_log2FC0.5-completeCase.csv")
```

```{r Epithelial like - GOS}
cc.gos <- clusterProfiler::simplify(cc.go, cutoff=0.05, by= "p.adjust")
dotplot(cc.gos, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_Ery_GOSimplified_log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")
```

```{r Lymphocyte 2 - PW}
cc.pw <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist[23:24],
                                         fun = "enrichPathway",
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')

dotplot(cc.pw, showCategory = 5) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, size = 10, face = "bold")) + 
  theme(axis.text.y = element_text(size = 13)) + 
  scale_color_viridis(direction = -1, trans="log10") 
ggsave("./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Ery-log2FC0.5-completeCase.png", width = 11, height = 11, units = "in")

write.csv(cc.pw@compareClusterResult, "./revisedDataset/clusterProfiler/clusterProfiler_enrichPathway_Ery_log2FC0.5-completeCase.csv")
```





