---
title: "FLC snRNA-seq clustering"
author: "Alaa R. Farghli"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Note:** This step was performed on a BioHPC "medium gen2: 40 cores, 256GB RAM" machine. I also performed this step on R 4.1.3, as R 4.2.1 cannot load the "stats" package for downstream steps

```{r load-libraries}
library(stringr)
library(Seurat)
library(tidyverse)
library(openxlsx)
library(scDblFinder)
library(BiocParallel)
```

```{r load-data}
set.seed(1234)

proj_name <- "FLCvNML"

##Setup the Seurat objects

# Load the counts matricies into separate datasets
N008.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_N008_filt/")
N014.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_N014_filt/")
N015.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_N015_filt/")
N021.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_N021_filt/")
T005.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_T005_filt/")
T008.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_T008_filt/")
T014.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_T014_filt/")
T015.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_T015_filt/")
T021.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_N021_filt/")
T034.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_T034_filt/")
T038.data <- Read10X(data.dir = "./soupx-adj-counts/soupx_T038_filt/")

# check for duplicated barcodes(column names) within a dataset
any(duplicated(x = colnames(x = N008.data))) # FALSE
any(duplicated(x = colnames(x = N014.data))) # FALSE
any(duplicated(x = colnames(x = N015.data))) # FALSE
any(duplicated(x = colnames(x = N021.data))) # FALSE
any(duplicated(x = colnames(x = T005.data))) # FALSE
any(duplicated(x = colnames(x = T008.data))) # FALSE
any(duplicated(x = colnames(x = T014.data))) # FALSE
any(duplicated(x = colnames(x = T015.data))) # FALSE
any(duplicated(x = colnames(x = T021.data))) # FALSE
any(duplicated(x = colnames(x = T034.data))) # FALSE
any(duplicated(x = colnames(x = T038.data))) # FALSE

# Rename columns to avoid trouble when merging data sets (since identical columns between KO and WT)
colnames(x = N008.data) <- paste('NML_N008', colnames(x = N008.data), sep = '_')
colnames(x = N014.data) <- paste('NML_N014', colnames(x = N014.data), sep = '_')
colnames(x = N015.data) <- paste('NML_N015', colnames(x = N015.data), sep = '_')
colnames(x = N021.data) <- paste('NML_N021', colnames(x = N021.data), sep = '_')

colnames(x = T005.data) <- paste('FLC_T005', colnames(x = T005.data), sep = '_')
colnames(x = T008.data) <- paste('FLC_T008', colnames(x = T008.data), sep = '_')
colnames(x = T014.data) <- paste('FLC_T014', colnames(x = T014.data), sep = '_')
colnames(x = T015.data) <- paste('FLC_T015', colnames(x = T015.data), sep = '_')
colnames(x = T021.data) <- paste('FLC_T021', colnames(x = T021.data), sep = '_')
colnames(x = T034.data) <- paste('FLC_T034', colnames(x = T034.data), sep = '_')
colnames(x = T038.data) <- paste('FLC_T034', colnames(x = T038.data), sep = '_')
```

```{r Create Seurat Object}
### Initialize the Seurat object with the raw, non-normalized data
# Keep all genes expressed in >= 3 cells. 
# Keep all cells with at least 200 detected genes.
N008 <- CreateSeuratObject(counts = N008.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "N008")
N014 <- CreateSeuratObject(counts = N014.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "N014")
N015 <- CreateSeuratObject(counts = N015.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "N015")
N021 <- CreateSeuratObject(counts = N021.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "N021")
T005 <- CreateSeuratObject(counts = T005.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T005")
T008 <- CreateSeuratObject(counts = T008.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T008")
T014 <- CreateSeuratObject(counts = T014.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T014")
T015 <- CreateSeuratObject(counts = T015.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T015")
T021 <- CreateSeuratObject(counts = T021.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T015")
T034 <- CreateSeuratObject(counts = T034.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T034")
T038 <- CreateSeuratObject(counts = T038.data, 
                            min.cells = 3, 
                            min.features = 200, 
                            project = "T038")
```

```{r Add group status to Seurat objects}
### add treatment/group status to objects
# add group
N008[["status"]] <- "NML"
N014[["status"]] <- "NML"
N015[["status"]] <- "NML"
N021[["status"]] <- "NML"
T005[["status"]] <- "FLC"
T008[["status"]] <- "FLC"
T014[["status"]] <- "FLC"
T015[["status"]] <- "FLC"
T021[["status"]] <- "FLC"
T034[["status"]] <- "FLC"
T038[["status"]] <- "FLC"

N008[["id"]] <- "N008"
N014[["id"]] <- "N014"
N015[["id"]] <- "N015"
N021[["id"]] <- "N021"
T005[["id"]] <- "T005"
T008[["id"]] <- "T008"
T014[["id"]] <- "T014"
T015[["id"]] <- "T015"
T021[["id"]] <- "T021"
T034[["id"]] <- "T034"
T038[["id"]] <- "T034"

N008
N014
N015
N021
T005
T008
T014
T015
T021
T034
T038
```

```{r Merge dataset, cache = T}
set.seed(1234)

# Merge datasets into one single seurat object
alldata <- merge(N008, y = c(N014, N015, N021, 
                             T005, T008, T014, T015, T021, T034, T038), 
                 add.cell.ids = c("N008", "N014", "N015", "N021", 
                             "T005", "T008", "T014", "T015", "T021", "T034", "T038"),
                 project = "fullFLC")

alldata

# Convert to single cell experiment
sce <- as.SingleCellExperiment(alldata)
```

```{r Run scDoubletFinder}
bp <- MulticoreParam(20, RNGseed=1234)
bpstart(bp)
sce <- scDblFinder(sce, 
                   samples="id", 
                   BPPARAM=bp)

bpstop(bp)

# If the code above doesn't work, unhash and try this.

#sce <- scDblFinder(sce,
#                   samples="id",
#                   BPPARAM=MulticoreParam(3))

table(sce$scDblFinder.class)

# Write out metadata of doublet scores to flat file
sce@colData %>% 
  as.data.frame() %>%
  rownames_to_column(var = "cell_id") %>%
  dplyr::select(cell_id, contains("scDblFinder")) %>%
  write_csv(paste0(proj_name, "_scDbtFinder_metadata.csv"))


sce_sub <- subset(sce, ,scDblFinder.class=="singlet")
table(sce_sub$scDblFinder.class)

singlet_cell_id <- colnames(sce_sub)
```

```{r}
saveRDS(alldata, "./alldata.rds")
saveRDS(sce, "./sce.rds")
sce <- readRDS("./sce.rds")
```

```{r}
for (i in 1:length(singlet_cell_id)) {
  singlet_cell_id[i] <- substr(singlet_cell_id[i], 6, nchar(singlet_cell_id[i]))
}
```

```{r}
# The [[ operator can add columns to object metadata. This is a great place to stash QC stats
alldata[["percent.mt"]] <- PercentageFeatureSet(alldata, pattern = "^MT-")
```

```{r}
# Visualize QC metrics as a violin plot
VlnPlot(alldata, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

```{r}
# FeatureScatter is typically used to visualize feature-feature relationships, but can be used
# for anything calculated by the object, i.e. columns in object metadata, PC scores etc.

plot1 <- FeatureScatter(alldata, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(alldata, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1 + plot2
```


### QC and filtering

```{r qc-and-filtering, fig.width = 5, fig.height = 6}
set.seed(1234)
# Calculate percentage of mitochondrial counts
obj.list <- list(N008, N014, N015, N021, T005, T008, T014, T015, T021, T034, T038)

# Remove cells classified as doublets by scDblFinder
for (i in 1:length(obj.list)) {
  print(obj.list[[i]]@project.name)
  print(paste0("Number of cells: ", ncol(obj.list[[i]])))
  obj.list[[i]] <- obj.list[[i]][,intersect(colnames(obj.list[[i]]), singlet_cell_id)]
  print(paste0("Number of cells: ", ncol(obj.list[[i]])))
  print(" ")
}

# Add % of reads mapping to mitochondrial genes
for (i in 1:length(obj.list)) {
  obj.list[[i]] <- PercentageFeatureSet(obj.list[[i]], pattern = "^MT-", col.name = 'percent.mt') 
  obj.list[[i]][["per.mito.bin"]] <- ifelse(obj.list[[i]][["percent.mt"]] > 20, "> 20%", ifelse(obj.list[[i]][["percent.mt"]] > 10, "10%-20%", ifelse(obj.list[[i]][["percent.mt"]] > 2.5, "2.5%-10%", "< 2.5%")))
}

# Visualize QC metrics as a violin plot
plts <- lapply(obj.list, function(x) VlnPlot(x, 
                                             features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), 
                                             group.by = "id",
                                             pt.size = 0,
                                             ncol = 3))

patchwork::wrap_plots(plts, ncol = 1)
ggsave(paste0(proj_name, "_QC_no-pts.png"), units = "in", width = 5, height = 4 * length(obj.list), dpi = 300)

plts <- lapply(obj.list, function(x) VlnPlot(x, 
                                             features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), 
                                             group.by = "id",
                                             pt.size = 0.25,
                                             ncol = 3))

patchwork::wrap_plots(plts, ncol = 1)
ggsave(paste0(proj_name, "_QC.png"), units = "in", width = 5, height = 4 * length(obj.list), dpi = 300)

# Subset loop

for (i in 1:length(obj.list)) {
  print(obj.list[[i]]@project.name)
  print(paste0("Number of cells: ", ncol(obj.list[[i]])))
  obj.list[[i]] <- subset(obj.list[[i]], subset = nFeature_RNA > 1000 & percent.mt < 20)
  print(paste0("Number of cells: ", ncol(obj.list[[i]])))
  print(" ")
}
```

```{r}
nFeature_RNA > 1000 & percent.mt < 25
 "N008"
 "Number of cells: 21713"
 "Number of cells: 18082"
 " "
 "N014"
 "Number of cells: 16844"
 "Number of cells: 8702"
 " "
 "N015"
 "Number of cells: 17425"
 "Number of cells: 15490"
 " "
 "N021"
 "Number of cells: 20046"
 "Number of cells: 16535"
 " "
 "T005"
 "Number of cells: 25734"
 "Number of cells: 17382"
 " "
 "T008"
 "Number of cells: 23090"
 "Number of cells: 14735"
 " "
 "T014"
 "Number of cells: 27915"
 "Number of cells: 18958"
 " "
 "T015"
 "Number of cells: 29013"
 "Number of cells: 23140"
 " "
 "T015"
 "Number of cells: 20046"
 "Number of cells: 16535"
 " "
 "T034"
 "Number of cells: 24953"
 "Number of cells: 13880"
 " "
"T038"
"Number of cells: 5026"
"Number of cells: 3892"

```

```{r}
nFeature_RNA > 1000 & percent.mt < 20
 "N008"
 "Number of cells: 18130"
 "Number of cells: 14503"
 " "
 "N014"
 "Number of cells: 14662"
 "Number of cells: 6625"
 " "
 "N015"
 "Number of cells: 14426"
 "Number of cells: 12491"
 " "
 "N021"
 "Number of cells: 17637"
 "Number of cells: 14132"
 " "
 "T005"
 "Number of cells: 22116"
 "Number of cells: 14172"
 " "
 "T008"
 "Number of cells: 18612"
 "Number of cells: 10388"
 " "
 "T014"
 "Number of cells: 23717"
 "Number of cells: 14875"
 " "
 "T015"
 "Number of cells: 24322"
 "Number of cells: 18475"
 " "
 "T015"
 "Number of cells: 17742"
 "Number of cells: 14231"
 " "
 "T034"
 "Number of cells: 20718"
 "Number of cells: 10490"
 " "
 "T038"
 "Number of cells: 4564"
 "Number of cells: 3457"
 " "
```

### SC Transform

The latest version of sctransform also supports using glmGamPoi package which substantially improves the speed of the learning procedure. It can be invoked by specifying method="glmGamPoi".

```{r sctransform, cache=T, message=F}
set.seed(1234)
obj.list <- lapply(X = obj.list, FUN = function(x) {
    x <- SCTransform(x, 
                     method = "glmGamPoi", 
                     assay = "RNA",
                     new.assay.name = "SCT")
})

features <- SelectIntegrationFeatures(object.list = obj.list, nfeatures = 3000)
obj.list <- PrepSCTIntegration(object.list = obj.list, anchor.features = features)

saveRDS(obj.list, "./objlist.rds")

integration.anchors <- FindIntegrationAnchors(object.list = obj.list, normalization.method = "SCT", anchor.features = features)

# saveRDS(integration.anchors, "./integrationanchors.rds")
integration.anchors <- readRDS("./integrationanchors.rds")

seurat_obj <- IntegrateData(anchorset = integration.anchors, normalization.method = "SCT")
saveRDS(seurat_obj, "./integrated-seurat-obj.rds")
```
### Clustering and visualization

The Seurat SCT vignette states that 30 PCs should be used, as this will increase performance.

```{r clustering, message=F}
set.seed(1234)
# Run the standard workflow for visualization and clustering
seurat_obj <- RunPCA(seurat_obj)
seurat_obj <- RunUMAP(seurat_obj, reduction = "pca", dims = 1:30)

seurat_obj <- FindNeighbors(seurat_obj, reduction = "pca", dims = 1:30)

saveRDS(seurat_obj, "./neighbors-seurat-obj.rds")
seurat_obj <- readRDS()

dir.create("res_iter")

for (i in seq(.1, 1.5, by = .1)) {
  seurat_obj_tmp <- FindClusters(seurat_obj, resolution = i)
  DimPlot(seurat_obj_tmp, reduction = "umap", label = T)
  ggsave(paste0("res_iter/", proj_name, '_res-iter_', i, '_umap.png'), units = 'in', width = 6, height = 5, dpi = 250)
}

seurat_obj <- FindClusters(seurat_obj, resolution = 0.7)

### Set default assay to RNA
DefaultAssay(seurat_obj) <- "RNA"
seurat_obj <- NormalizeData(seurat_obj)
seurat_obj <- ScaleData(seurat_obj)

saveRDS(seurat_obj, paste0(proj_name, '_seurat-obj.rds'))
seurat_obj <- readRDS(file = "./FLCvNML_seurat-obj.rds")
```


```{r UMAP-plot, fig.width=6, fig.height=10}
### Make UMAP plots

plt1 <- DimPlot(seurat_obj, reduction = "umap", label = T)
plt2 <- DimPlot(seurat_obj, reduction = "umap", group.by = "status")
plt1 / plt2
ggsave(paste0(proj_name, '_umap.png'), units = 'in', width = 6, height = 10, dpi = 250)

```


```{r UMAP-extra-metrics, fig.width=6, fig.height=30}
### Add additional metadata
seurat_obj[["scDblFinder.scores"]] <- sce_sub[,colnames(seurat_obj)]$scDblFinder.score
seurat_obj <- CellCycleScoring(
    seurat_obj,
    s.features = str_to_title(cc.genes$s.genes),
    g2m.features = str_to_title(cc.genes$g2m.genes),
    assay = 'SCT',
    set.ident = TRUE
  )
Idents(seurat_obj) <- "seurat_clusters"

### Plot metadata
plt1 <- DimPlot(seurat_obj, reduction = "umap", label = T)
plt2 <- DimPlot(seurat_obj, reduction = "umap", group.by = "status")
plt3 <- DimPlot(seurat_obj, reduction = "umap", group.by = "per.mito.bin")
plt4 <- FeaturePlot(seurat_obj, features = "scDblFinder.scores")
plt5 <- DimPlot(seurat_obj, reduction = "umap", group.by = "id")
plt1 / plt2 / plt3 / plt5
ggsave(paste0(proj_name, '_umap_other-meta.png'), units = 'in', width = 6, height = 30, dpi = 250)

```


```{r cell-abundances}

### Find cell #/% in each cluster and right output

count_per_cluster <- table(Idents(seurat_obj), seurat_obj@meta.data$status)
percent_per_cluster <- prop.table(table(Idents(seurat_obj), seurat_obj@meta.data$status), margin = 2)

count_per_cluster
percent_per_cluster

as.data.frame(percent_per_cluster) %>%
  mutate(Percent = Freq * 100,
         Cluster = Var1,
         Condition = Var2) %>%
  ggplot(., aes(Cluster, Percent, fill = Condition)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  theme_classic()
  ggsave(paste0(proj_name, '_percent_cell_in_cluster.png'), width = 8, height = 6)

as.data.frame(prop.table(table(Idents(seurat_obj), seurat_obj@meta.data$status), margin = 1)) %>%
    mutate(Percent = Freq * 100,
         Cluster = Var1,
         Condition = Var2) %>%
  ggplot(., aes(Cluster, Percent, fill = Condition)) +
  geom_bar(stat = 'identity') +
  theme_classic()
  ggsave(paste0(proj_name, '_percent_sample_in_cluster.png'), width = 8, height = 6)


wb=createWorkbook()
ws=addWorksheet(wb,'Cells per cluster')
writeData(wb, ws, count_per_cluster, rowNames = F, colNames = T, startRow = 1,startCol = 1)
ws=addWorksheet(wb,'Percent per cluster')
writeData(wb, ws, percent_per_cluster, rowNames = F, colNames = T, startRow = 1,startCol = 1)
saveWorkbook(wb, paste0(proj_name, '_cells_per_cluster.xlsx'), overwrite = T)

```

## Session info

```{r session-info}

sessionInfo()

```
