---
title: "FLC snRNA-seq clustering"
author: "Alaa R. Farghli"
date: "Last compiled on `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries}
library(Seurat)
library(tidyverse)
```
# Single cell RNAseq analysis

This is the continued single nuclei RNAseq analysis of FLC provided by the Khasayer lab.

## Seurat analysis

### Find markers

```{r find-markers, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r}
harmonized.seurat <- readRDS(paste0("rds/", proj_name, '_harmonized-byID-obj.rds'))
Idents(harmonized.seurat) <- "seurat_clusters"
levels(harmonized.seurat)
harmonized.seurat <- PrepSCTFindMarkers(harmonized.seurat)

markers <- FindAllMarkers(harmonized.seurat, 
                          assay = "RNA",
                          min.pct = -Inf, 
                          logfc.threshold = .5, 
                          only.pos = T, 
                          test.use = "wilcox",
                          latent.vars = c('percent.mt', 'nFeature_RNA'))

dir.create("markers")
markers <- markers %>%
  filter(avg_log2FC > 0) %>%
  write_csv(paste0("markers", proj_name, '_HighlyEnrichedMarkers_logFC.5_wilcox-12cluster.csv'))
markers <- read_csv(paste0("markers", proj_name, '_HighlyEnrichedMarkers_logFC.5_wilcox-12cluster.csv'))
head(markers)
```

## Determine and assign cell type

### Overlap of cluster markers with markers of known cell types

This is a custom function the checks the percent overlap between a marker gene list of a certain cell type with the markers of each cluster (as determined by the FindMarkers function).

```{r functions}
geneset_marker_overlap.f <- function(SerObj, enrichedGenes_df, known_markers, FC_thresh = 0, projname = 'proj', w = NULL, h = NULL, facet_ncol = 5, save_plot = T) {

  ### Loop through each cluster and calculate the percentage of genes from each cell type in that cluster
  #     above the FC_thresh using the output from finding highly enriched markers of each cluster
  overlap_df <- data.frame()
  for (i in sort(unique(Idents(SerObj)))) {
    cat(paste0('\nCalculating geneset percentages for cluster ', i, '...'))
    df_tmp <- enrichedGenes_df %>%
      filter(cluster == i) %>%
      filter(avg_log2FC > FC_thresh)

    for (t in unique(sort(known_markers$type))) {

      cell_type_markers <- known_markers %>%
        filter(type == t) %>%
        pull(gene) %>%
        unique() %>%
        as.vector()

      per <- length(intersect(df_tmp$gene, cell_type_markers)) / length(cell_type_markers) * 100
      genes <- intersect(df_tmp$gene, cell_type_markers)

      overlap_df <- bind_rows(overlap_df, data.frame('Cluster' = i,
                                                     'Type' = t,
                                                     'Percent' = round(per, 2),
                                                     'Overlap_genes' = paste(genes, collapse = '|'),
                                                     'number_of_cluster_markers' = length(df_tmp$gene)))
    }
  }
  cat('\n\n')
  
  ### Reformat the dataframe to be easier to read, write to csv, and return
  overlap_df %>%
    dplyr::select(Cell_Type = Type, everything()) %>%
    write_csv(paste0(projname, '_FC', FC_thresh, '.csv'))

  ### Refactor cluster so appear in numerical order
  overlap_df <- overlap_df %>%
    mutate(Cluster = factor(Cluster, levels = unique(Cluster)))

  ### Create a bar plot to show the percent cell type cells present in each cluster
  overlap_df <- overlap_df %>%
    mutate(facet_name = paste0(Cluster, " (", number_of_cluster_markers, ")"))

  overlap_df$facet_name <- reorder(overlap_df$facet_name, as.numeric(overlap_df$Cluster))

  # Plot
  g <- ggplot(overlap_df, aes(Type, Percent, alpha = Percent)) +
          geom_bar(stat = 'identity', color = 'black') +
          facet_wrap(~facet_name, ncol = facet_ncol, scales = 'free_y') +
          scale_x_discrete(NULL) +
          theme_bw() +
          theme(text = element_text(size = 20),

                axis.title = element_text(size = 18, face = 'bold'),
                axis.text.y = element_text(size = 16, color = 'black'),
                axis.text.x = element_text(size = 16, color = 'black', angle = 90, hjust = 1, vjust = .5),

                strip.text = element_text(face = 'bold'),

                panel.grid = element_blank())
  
  if (save_plot == T) {
      filename = paste0(projname, '_FC', FC_thresh, '.png')
      print(paste0('Saving percent image as: ', filename))



  # Determine width and height
  if (is.null(w)) {
    w = min(10, length(unique(overlap_df$Cluster)) * 1.75 + 3)
  }

  if (is.null(h)) {
    h = max(3, 2 * ceiling(length(unique(overlap_df$Cluster)) / 5))
  }
      
      g
      ggsave(filename, width = w, height = h)
      
  }


  return(g)
}
```



```{r cell-type-markers, fig.width=12, fig.height=8}
dir.create("cell_type_assignment")
cell_marker_dir <- "./"

## Haber
cell_markers <- read_csv("./liverMarkers.csv") %>% 
  dplyr::rename(type = cluster) %>% 
  dplyr::rename(gene = name)

geneset_marker_overlap.f(harmonized.seurat,
                         markers,
                         cell_markers,
                         FC_thresh = .5, 
                         projname = paste0("cell_type_assignment/", proj_name, '_CTA_Macparland_12clusters'))

# Non-core scRNA analysis code, specifically to check for FLC
flc <- data.frame(type = "FLC", gene = c("MIR10B", "VCAN", "SLC16A14", "LINC00473", "MIR375", "PDE10A", "MARCH10", "FAM19A5", "FURIN", "EGFLAM", "PDE4B", "TMEM163", "OAT", "NOVA1", "TESC", "RPS6KA2", "CA12"))

geneset_marker_overlap.f(harmonized.seurat,
                         markers,
                         flc,
                         FC_thresh = .5, 
                         projname = paste0("cell_type_assignment/", proj_name, '_CTA_FLC_12clusters'))


```

### Cumulative expression of cell type marker list across clusters

For a list of cell type markers, calculate a expression score for each cluster. An in-depth explaination of what is happening in the AddModuleScore function can be found in a [blog post by Walter Muskovic](https://www.waltermuskovic.com/2021/04/15/seurat-s-addmodulescore-function/).

```{r module-expression, warning=F}
# We create a temporary Seurat object here to avoid over populating our metadata with these scores
harmonized.seurat_tmp <- harmonized.seurat

## Haber
cell_markers <- read_csv("./liverMarkers.csv") %>% 
  dplyr::rename(type = cluster) %>% 
  dplyr::rename(gene = name)

goi_li <- split(cell_markers$gene, cell_markers$type)
harmonized.seurat_tmp <- AddModuleScore(object = harmonized.seurat, features = goi_li, name = "MarkerList")

DotPlot(harmonized.seurat_tmp, features = paste0("MarkerList", seq(1, length(goi_li)))) +  
  scale_x_discrete(NULL,
                   labels = names(goi_li)) +
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1))

ggsave(paste0("cell_type_assignment/", proj_name, "_DP-CTA_Macparland-module.png"), units = "in", width = 2 + length(goi_li) * .75, height = 8)

## IEL
cell_markers <- data.frame(type = "FLC", gene = c("MIR10B", "VCAN", "SLC16A14", "LINC00473", "MIR375", "PDE10A", "MARCH10", "FAM19A5", "FURIN", "EGFLAM", "PDE4B", "TMEM163", "OAT", "NOVA1", "TESC", "RPS6KA2", "CA12"))

goi_li <- split(cell_markers$gene, cell_markers$type)
seurat_tmp <- AddModuleScore(object = seurat_tmp, features = goi_li, name = "MarkerList")

DotPlot(seurat_tmp, features = paste0("MarkerList", seq(1, length(goi_li)))) + 
  scale_x_discrete(NULL,
                   labels = names(goi_li)) +
  theme(axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1))

ggsave(paste0("cell_type_assignment/", proj_name, "_DP-CTA_FLC.png"), units = "in", width = 3 + length(goi_li) * .75, height = 8)
```


### Assign cell types

Based on the results of the overlap analysis and the module expression scores, we can assign cell types. This is curated manually and saved as a <name>_cluster_assignment.csv file.


```{r cell-type-assignment}
cluster_ass <- read_csv(paste0(proj_name, '_cluster_assignment.csv')) %>%
  mutate(cluster_assignment = paste(cluster, assignment, sep = "_"))

seurat_obj[["cluster_id_named"]] <- plyr::mapvalues(Idents(seurat_obj),
                                                    from=cluster_ass$cluster,
                                                    to=cluster_ass$cluster_assignment)

new.cluster.ids <- cluster_ass$assignment
names(new.cluster.ids) <- levels(seurat_obj)
seurat_obj <- RenameIdents(seurat_obj, new.cluster.ids)

seurat_obj[["cluster_named"]] <- Idents(seurat_obj)


DimPlot(seurat_obj, reduction = "umap", label = TRUE, pt.size = 0.5) + NoLegend()
ggsave(paste0(proj_name, "_umap_clusterNamed.png"), units = 'in', width = 6, height = 6, dpi = 250)


# Save a cluster named and a cluster named without immune
saveRDS(seurat_obj, paste0(proj_name, '_seurat-obj.rds'))
```

### Find markers of named clusters

```{r find-markers-named, warning=F}

markers <- FindAllMarkers(seurat_obj, 
                          min.pct = -Inf, 
                          logfc.threshold = .25, 
                          only.pos = T, 
                          test.use = "MAST",
                          latent.vars = c('percent.mt', 'nFeature_RNA'))

markers <- markers %>%
  filter(avg_log2FC > 0) %>%
  write_csv(paste0(proj_name, '_HighlyEnrichedMarkers_CLUSTERNAMED_logFC.25.csv'))

```

## Session info

```{r session-info}

sessionInfo()

```