---
title: "Combined cellchat analysis"
output: html_document
date: "2024-01-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries}
library(Seurat)
library(tidyverse)
library(CellChat)
library(patchwork)
library(svglite)
library(ggalluvial)
library(NMF)
library(reticulate)
options(stringsAsFactors = FALSE)
```

```{r set seed and project name, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r}
flc.cellchat <- readRDS(file = "./fullDataset/rds/scRNA_FLCnew-2.rds")
nml.cellchat <- readRDS(file = "./fullDataset/rds/scRNA_NMLnew-2.rds")
object.list <- list(NML = nml.cellchat, FLC = flc.cellchat)
cellchat.combined <- readRDS("./revisedDataset/cellChat/merged/FLC_NML_combinedCellchat.rds")
```

```{r}
## This is done with the alternative approach to getting counts, which is normalizing the RNA and then separating by tissue status
dir.create("./revisedDataset/cellChat/merged")
dir.create("./revisedDataset/cellChat/merged/plots")
```

```{r Combine both cellchat objects}
cellchat.combined <- mergeCellChat(object.list, add.names = names(object.list), merge.data = FALSE)
```

## Part I: Predict general principles of cell-cell communication

```{r}
gg1 <- compareInteractions(cellchat.combined, show.legend = F, group = c(1,2), x.lab.rot = TRUE, angle.x = 90)
gg2 <- compareInteractions(cellchat.combined, show.legend = F, group = c(1,2), measure = "weight")
png(file ="./revisedDataset/cellChat/merged/plots/Number_strength-compareInteractions.png", width = 5, height = 4, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
gg1 <- netVisual_diffInteraction(cellchat.combined, weight.scale = T)
gg2 <- netVisual_diffInteraction(cellchat.combined, weight.scale = T, measure = "weight")
png(file ="./revisedDataset/cellChat/merged/plots/Number_strength-Circleplot.png", width = 10, height = 4, units = "in", res = 600)
gg1
gg2
dev.off()
```

```{r}
gg1 <- netVisual_heatmap(cellchat.combined)
#> Do heatmap based on a merged object
gg2 <- netVisual_heatmap(cellchat.combined, measure = "weight")
#> Do heatmap based on a merged object
png(file ="./revisedDataset/cellChat/merged/plots/Number_strength-heatmap.png", width = 8, height = 6, units = "in", res = 600)
gg1 + gg2
dev.off()
```
```{r}
png(file ="./revisedDataset/cellChat/merged/plots/Number_byStatus_circlePlot.png", width = 7, height = 4, units = "in", res = 600)
weight.max <- getMaxWeight(object.list, attribute = c("idents","count"))
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_circle(object.list[[i]]@net$count, weight.scale = T, label.edge= F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = paste0("Number of interactions - ", names(object.list)[i]))
}
dev.off()

png(file ="./revisedDataset/cellChat/merged/plots/Number_byStatus_NML.png", width = 10, height = 10, units = "in", res = 600)
netVisual_circle(object.list$NML@net$count, weight.scale = T, label.edge = F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name =  "Number of interactions - NML")
dev.off()

netVisual_circle(object.list$FLC@net$count, weight.scale = T, label.edge = F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = "Number of interactions - FLC")
```


```{r}
num.link <- sapply(object.list, function(x) {rowSums(x@net$count) + colSums(x@net$count)-diag(x@net$count)})
weight.MinMax <- c(min(num.link), max(num.link)) # control the dot size in the different datasets
gg <- list()
for (i in 1:length(object.list)) {
  gg[[i]] <- netAnalysis_signalingRole_scatter(object.list[[i]], title = names(object.list)[i], weight.MinMax = weight.MinMax)
}
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways

png(file ="./revisedDataset/cellChat/merged/plots/SignalingRoleByStatus_heatmap.png", width = 9, height = 4, units = "in", res = 600)
patchwork::wrap_plots(plots = gg)
dev.off()
```
```{r}
num.link <- sapply(object.list, function(x) {rowSums(x@net$count) + colSums(x@net$count)-diag(x@net$count)})
weight.MinMax <- c(min(num.link), max(num.link)) # control the dot size in the different datasets
gg <- list()
for (i in 1:length(object.list)) {
  gg[[i]] <- netAnalysis_signalingRole_scatter(object.list[[i]], title = names(object.list)[i], weight.MinMax = weight.MinMax, signaling = c("FGF",))
}
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways

png(file ="./revisedDataset/cellChat/merged/plots/SignalingRole_F_heatmap.png", width = 9, height = 4, units = "in", res = 600)
patchwork::wrap_plots(plots = gg)
dev.off()
```

```{r}
gg1 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Endothelial cells", signaling.label = c("PDGF", "TGFb"), dot.size = 2)
gg2 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Neutrophils and macrophages", signaling.label = "TGFb", dot.size = 2)
gg3 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Stellate cells", signaling.label = c("TGFb"), dot.size = 2, top.label = .6)
png(file ="./revisedDataset/cellChat/merged/plots/SignalingChanges_scatter.png", width = 18, height = 4, units = "in", res = 600)
patchwork::wrap_plots(plots = list(gg1,gg2,gg3))
dev.off()
```

```{r}
gg2 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Stellate cells", signaling = c("FGF", "CALCR"))
```


### Identify signaling groups based on their functional similarity

```{r}
use_python("/home/af547/miniconda3/bin/python")
cellchat.combined <- computeNetSimilarityPairwise(cellchat.combined, type = "functional")
cellchat.combined <- netEmbedding(cellchat.combined, type = "functional")
cellchat.combined <- netClustering(cellchat.combined, type = "functional", do.parallel = FALSE)
netVisual_embeddingPairwise(cellchat.combined, type = "functional", label.size = 3.5)
```
```{r}
cellchat.combined <- computeNetSimilarityPairwise(cellchat.combined, type = "structural")
cellchat.combined <- netEmbedding(cellchat.combined, type = "structural")
cellchat.combined <- netClustering(cellchat.combined, type = "structural", do.parallel = FALSE)
# Visualization in 2D-space
netVisual_embeddingPairwise(cellchat.combined, type = "structural", label.size = 3.5)
netVisual_embeddingPairwiseZoomIn(cellchat.combined, type = "structural", nCol = 2)
```

### Compute and visualize the pathway distance in the learned joint manifold

```{r}
png(file ="./revisedDataset/cellChat/merged/plots/RankSimilarity.png", width = 3, height = 3, units = "in", res = 600)
rankSimilarity(cellchat.combined, type = "functional")
dev.off()
#> Compute the distance of signaling networks between datasets 1 2
```

### Identify and visualize the conserved and context-specific signaling pathways

#### Compare the overall information flow of each signaling pathway

```{r}
gg1 <- rankNet(cellchat.combined, mode = "comparison", stacked = T, do.stat = TRUE)
gg2 <- rankNet(cellchat.combined, mode = "comparison", stacked = F, do.stat = TRUE)
png(file ="./revisedDataset/cellChat/merged/plots/RankNet.png", width = 7, height = 3, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
library(ComplexHeatmap)
i = 1
pathway.union <- union(object.list[[i]]@netP$pathways, object.list[[i+1]]@netP$pathways)
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6)
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 6)
png(file ="./revisedDataset/cellChat/merged/plots/OutgoingSignalingRole_heatmap.png", width = 8, height = 6, units = "in", res = 600)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6, color.heatmap = "GnBu")
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 6, color.heatmap = "GnBu")
png(file ="./revisedDataset/cellChat/merged/plots/IncomingSignalingRole_heatmap.png", width = 8, height = 6, units = "in", res = 600)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "all", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6, color.heatmap = "OrRd")
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "all", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 6, color.heatmap = "OrRd")
png(file ="./revisedDataset/cellChat/merged/plots/AllSignalingRole_heatmap.png", width = 8, height = 6, units = "in", res = 600)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

### Part III: Identify the upgulated and down-regulated signaling ligand-receptor pairs 

```{r}
netVisual_bubble(cellchat.combined, signaling = "PDGF", comparison = c(1, 2), angle.x = 45)
#> Comparing communications on a merged object
```
```{r}
gg1 <- netVisual_bubble(cellchat.combined, sources.use = 4, targets.use = c(5:11),  comparison = c(1, 2), max.dataset = 2, title.name = "Increased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg2 <- netVisual_bubble(cellchat.combined, sources.use = 4, targets.use = c(5:11),  comparison = c(1, 2), max.dataset = 1, title.name = "Decreased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg1 + gg2
```


#### Identify dysfunctional signaling by using differential expression analysis

```{r}
pos.dataset = "FLC"
features.name = paste0(pos.dataset, ".merged")
```

```{r}
cellchat.combined <- identifyOverExpressedGenes(cellchat.combined, group.dataset = "datasets", pos.dataset = pos.dataset, features.name = features.name, only.pos = FALSE, thresh.pc = 0.1, thresh.fc = 0.05,thresh.p = 0.05) 
```
```{r}
net <- netMappingDEG(cellchat.combined, features.name = features.name)
net.up <- subsetCommunication(cellchat.combined, net = net, datasets = "FLC",ligand.logFC = 0.05, receptor.logFC = NULL)
net.down <- subsetCommunication(cellchat.combined, net = net, datasets = "NML",ligand.logFC = -0.05, receptor.logFC = NULL)
```

```{r}
gene.up <- extractGeneSubsetFromPair(net.up, cellchat.combined)
gene.down <- extractGeneSubsetFromPair(net.down, cellchat.combined)
```

```{r}
pairLR.use.up = net.up[, "interaction_name", drop = F]
gg1 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.up, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
gg2 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.down, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object

png(file ="./revisedDataset/cellChat/merged/plots/Upregulated-downregulated_dotplot.png", width = 10, height = 6, units = "in", res = 600)
gg1 + gg2
dev.off()
```


```{r}
netVisual_bubble(cellchat.combined, signaling = c("PDGF", "TGFb"), comparison = c(1, 2), angle.x = 45)
#> Comparing communications on a merged object
```

```{r}
netVisual_bubble(cellchat.combined, signaling = "PDGF", comparison = c(1, 2), angle.x = 45)
```
```{r}
netVisual_bubble(cellchat.combined, signaling = "TGFb", comparison = c(1, 2), angle.x = 45)
```

### Identify the upgulated (increased) and down-regulated (decreased) signaling ligand-receptor pairs 

```{r PDGF l-r pairs}
gg1 <- netVisual_bubble(cellchat.combined, signaling = "PDGF", max.dataset = 2, title.name = "Increased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg2 <- netVisual_bubble(cellchat.combined, signaling = "PDGF", max.dataset = 1, title.name = "Decreased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg1 + gg2
```


```{r}
pathways.show <- c("PERIOSTIN") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

### Visually compare cell to cell communication

```{r}
pathways.show <- c("FGF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

```{r}
pathways.show <- c("FGF") 
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
```

### Part IV: Visually compare cell-cell communication using Hierarchy plot, Circle plot or Chord diagram

#### PDGF
```{r}
dir.create("./revisedDataset/cellChat/merged/plots/PDGF")
```

```{r}
pathways.show <- c("PDGF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
png(file ="./revisedDataset/cellChat/merged/plots/PDGF/PDGF_heatmap.png", width = 8, height = 6, units = "in", res = 600)
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
png(file = paste0("./revisedDataset/cellChat/merged/plots/PDGF/", "PDGF_", i, "aggregateChord.png"), width = 8, height = 8, units = "in", res = 600)
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]))
}
dev.off()
```

#### TGFB
```{r}
dir.create("./revisedDataset/cellChat/merged/plots/TGFb")
```

```{r}
pathways.show <- c("TGFb") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
png(file ="./revisedDataset/cellChat/merged/plots/TGFb/TGFb_heatmap.png", width = 8, height = 6, units = "in", res = 600)
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
png(file = paste0("./revisedDataset/cellChat/merged/plots/TGFb/", "TGFb_", i, "aggregateChord.png"), width = 8, height = 8, units = "in", res = 600)
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]))
}
dev.off()
```

```{r}
cellchat.combined@meta$datasets = factor(cellchat.combined@meta$datasets, levels = c("NML", "FLC")) # set factor level
png(file ="./revisedDataset/cellChat/merged/plots/TGFb/TGFb_splitGeneExpression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat.combined, signaling = "TGFb", split.by = "datasets", colors.ggplot = T)
dev.off()
```

#### FGF
#### PDGF
```{r}
dir.create("./revisedDataset/cellChat/merged/plots/")
```

```{r}
pathways.show <- c("PDGF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
png(file ="./revisedDataset/cellChat/merged/plots/PDGF/PDGF_heatmap.png", width = 8, height = 6, units = "in", res = 600)
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
png(file = paste0("./revisedDataset/cellChat/merged/plots/PDGF/", "PDGF_", i, "aggregateChord.png"), width = 8, height = 8, units = "in", res = 600)
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]))
}
dev.off()
```

```{r}
cellchat.combined@meta$datasets = factor(cellchat.combined@meta$datasets, levels = c("NML", "FLC")) # set factor level
png(file ="./revisedDataset/cellChat/merged/plots/PDGF/PDGF_splitGeneExpression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat.combined, signaling = "PDGF", split.by = "datasets", colors.ggplot = T)
dev.off()
```


```{r}
saveRDS(cellchat.combined, "./revisedDataset/cellChat/merged/FLC_NML_combinedCellchat.rds")
```

