---
title: "New FLC subset for cellchat"
output: html_document
date: "2024-01-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries}
library(Seurat)
library(tidyverse)
library(CellChat)
library(patchwork)
library(svglite)
library(ggalluvial)
library(NMF)
library(reticulate)
options(stringsAsFactors = FALSE)
```

```{r set seed and project name, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r}
harmonized.seurat <- readRDS('./revisedDataset/rds/FLCvNML_Named-obj.rds')
```

```{r Extract RNA count table}
# Check available assays
assay_names <- Assays(harmonized.seurat)
print(assay_names)

# Extract data matrix
data_matrix <- GetAssayData(harmonized.seurat,  assay = "RNA") # normalized data matrix
```

```{r}
labels <- Idents(harmonized.seurat)
meta <-  harmonized.seurat@meta.data # a dataframe with rownames containing cell mata data
cell.use <-  rownames(meta)[meta$orig.ident == "FLC"]
```

```{r }
data.input <- data_matrix[, cell.use]
meta <-  meta[cell.use, ]
```

## Alternative way to get counts

```{r}
Idents(harmonized.seurat) <- harmonized.seurat$cluster_named
data.input <- NormalizeData(harmonized.seurat, normalization.method = "LogNormalize", scale.factor = 10000, assay = "RNA")
data.input <- subset(harmonized.seurat, subset = status == "FLC")
cellchat <- createCellChat(object = data.input, group.by = "cluster_named")
```


```{r}
levels(cellchat@idents) # show factor levels of the cell labels
groupSize <- as.numeric(table(cellchat@idents)) # number of cells in each cell group
```


```{r Set the ligand-receptor interaction database}
CellChatDB <- CellChatDB.human # use CellChatDB.mouse if running on mouse data
showDatabaseCategory(CellChatDB)
```

```{r}
dplyr::glimpse(CellChatDB$interaction)
CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling") # use Secreted Signaling
cellchat@DB <- CellChatDB.use
```

```{r Preprocessing the expression data for cell-cell communication analysis}
# subset the expression data of signaling genes for saving computation cost
cellchat <- subsetData(cellchat) # This step is necessary even if using the whole database
future::plan("multisession", workers = 70) # do parallel
cellchat <- identifyOverExpressedGenes(cellchat)
cellchat <- identifyOverExpressedInteractions(cellchat)
cellchat <- projectData(cellchat, PPI.human)
saveRDS(cellchat, "./fullDataset/rds/scRNA_FLCnew-1-alternate.rds")
cellchat <- readRDS("./fullDataset/rds/scRNA_FLCnew-1-alternate.rds")
```

```{r}
cellchat <- computeCommunProb(cellchat, type = "triMean", population.size = TRUE)
cellchat <- filterCommunication(cellchat, min.cells = 10)
cellchat <- computeCommunProbPathway(cellchat)
saveRDS(cellchat, "./fullDataset/rds/scRNA_FLCnew-2-alternate.rds")
cellchat <- readRDS("./fullDataset/rds/scRNA_FLCnew-2-alternate.rds")
```

```{r}
levels = c("Liver epithelial cells 1","Liver epithelial cells 2", "Liver epithelial cells 3", "Liver epithelial cells 4", "Liver epithelial cells 5", "Liver epithelial cells 6", "Endothelial cells", "Stellate cells", "Neutrophils and macrophages", "Lymphocytes", "Cholangiocyte cells", "Unknown") # set factor
flc.cellchat <- updateClusterLabels(flc.cellchat, new.order = levels)
levels(flc.cellchat@idents)
```
```{r}
cols <- c("Liver epithelial cells 1" = "#0072B2",
             "Liver epithelial cells 2" = "#cab2d6",
             "Endothelial cells" = "#6a3d9a",
             "Liver epithelial cells 3" = "#DDCC77",
             "Liver epithelial cells 4" = "#ff7f00",
             "Stellate cells" = "#33a02c",
             "Liver epithelial cells 5" = "#AA4499",
             "Cholangiocyte cells" = "#CC6677",
             "Neutrophils and macrophages" = "#44AA99",
             "Lymphocytes" = "#8C87E6",
             "Liver epithelial cells 6" = "#FF6B6B",
             "Unknown" = "#b15928")
```


```{r Calculate the aggregated cell-cell communication network}
dir.create("./revisedDataset/cellChat/FLCnew")
cellchat <- aggregateNet(cellchat)
groupSize <- as.numeric(table(cellchat@idents)) # number of cells in each cell group
levels(cellchat@idents)
```

```{r Subset the inferred cell-cell communications of interest}
df.net <- subsetCommunication(cellchat)
df_net <- subsetCommunication(cellchat, signaling = c(unique(df.net$pathway_name)), slot.name = "net")
df_net
write.csv(df.net, "./revisedDataset/cellChat/FLCnew/cellChat-allInferredCommunications.csv")
write.csv(df_net, "./revisedDataset/cellChat/FLCnew/cellChat-upregulatedPathways-ofInterest.csv")
```

## Calculate the aggregated cell-cell communication network
```{r}
dir.create("./revisedDataset/cellChat/FLCnew/plots")
groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions", shape = "circle", vertex.label.cex = .8, margin = .5)
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength", vertex.label.cex = .8, margin = .5)
```

```{r}
png("./revisedDataset/cellChat/FLCnew/plots/aggregatedCommunicationNetwork_NumberofInteractions_count.png", width = 6, height = 6, units = "in", res = 300)  # Adjust dimensions and resolution
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "FLC subset:Number of interactions", shape = "circle", vertex.label.cex = .8, margin = .5)
dev.off()
```

```{r}
png("./revisedDataset/cellChat/FLCnew/plots/aggregatedCommunicationNetwork_NumberofInteractions_weight.png", width = 6, height = 6, units = "in", res = 300)  # Adjust dimensions and resolution
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "FLC subset:Interaction weights/strength", vertex.label.cex = .8, margin = .5)
dev.off()
```

```{r}
mat <- cellchat@net$weight
par(mfrow = c(3,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}
```

```{r}
# Iterate through each row in mat
dir.create("./revisedDataset/cellChat/FLCnew/plots/cellTypeSignaling/")
for (i in 1:nrow(mat)) {
  # Create a new matrix with zeros and set the current row values
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  
  # Define the output file name
  output_filename <- paste0("./revisedDataset/cellChat/FLCnew/plots/cellTypeSignaling/", "FLCsubset-aggregatedCommunicationNetwork_byCell_weight", i, ".png")
  
  # Open a new graphics device and save the plot
  png(output_filename, width = 6, height = 6, units = "in", res = 300)
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = TRUE, edge.weight.max = max(mat), title.name = rownames(mat)[i])
  dev.off()
}
```

```{r }
# pathways showing significant communications
cellchat@netP$pathways
# Access all the signaling pathways showing significant communications
pathways.show.all <- cellchat@netP$pathways
dir.create("./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/")
for (i in pathways.show.all) {
  dir.create(paste0("./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/", i))
  }
```

```{r}
# check the order of cell identity to set suitable vertex.receiver
levels(cellchat@idents)
vertex.receiver = seq(3)
# Loop through pathways and save images in their respective directories
for (i in 1:length(pathways.show.all)) {
  pathway_dir <- pathways.show.all[i]
  dir_path <- paste0("./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/", pathway_dir)

  # Visualize communication network associated with both signaling pathway and individual L-R pairs
  netVisual(cellchat, signaling = pathway_dir, vertex.receiver = vertex.receiver, layout = "hierarchy")

  # Compute and visualize the contribution of each ligand-receptor pair to the overall signaling pathway
  gg <- netAnalysis_contribution(cellchat, signaling = pathway_dir)

  # Specify the full path for saving the image
  image_filename <- paste0(dir_path, "/", pathway_dir, "_FLCsubset_L-R_contribution.pdf")

  # Save the image in the pathway-specific directory
  ggsave(filename = image_filename, plot = gg, width = 5, height = 2, units = 'in', dpi = 300)
}
```

### PERIOSTIN analysis

```{r}
pathways.show <- c("PERIOSTIN") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLCchord_diagram.png", width = 22, height = 20, units = "cm", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLCchord_L-R_diagram.png", width = 13, height = 13, units = "cm", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("PERIOSTIN"), legend.pos.x = 8, lab.cex = 1.2)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PERIO <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PERIO[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLCchord_diagram_LRpair.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLC_PERIOSTIN_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("PERIOSTIN"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PERIOSTIN/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "PERIOSTIN", enriched.only = TRUE)
dev.off()
```

### Dissection of PDGF pathway

```{r}
pathways.show <- c("PDGF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLCchord_diagram.png", width = 22, height = 20, units = "cm", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLCchord_L-R_diagram.png", width = 17, height = 15, units = "cm", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("PDGF"), legend.pos.x = -20, legend.pos.y = 1, lab.cex = 1.5)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PDGF <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PDGF[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLCchord_diagram_LR_pair1.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLC_PDGF_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("PDGF"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/PDGF/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "PDGF", enriched.only = TRUE)
dev.off()
```

### FGF pathway dissection

```{r}
pathways.show <- c("FGF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(flc.cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(flc.cellchat, signaling = pathways.show, layout = "circle", color.use = cols)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLCchord_diagram.png", width = 7, height = 7, units = "in", res = 600)
netVisual_aggregate(flc.cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1, color.use = cols)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLCchord_L-R_diagram.png", width = 7, height = 7, units = "cm", res = 600)
netVisual_chord_gene(flc.cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("FGF"), legend.pos.x = -2, legend.pos.y = 5, lab.cex = 1.5, color.use = cols)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLC_heatmap.png", width = 5, height = 4.5, units = "in", res = 600)
netVisual_heatmap(flc.cellchat, signaling = pathways.show, color.heatmap = "Reds", color.use = cols)
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.FGF <- extractEnrichedLR(flc.cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.FGF[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLCchord_diagram_LR_pair1.png", width = 7, height = 7, units = "in", res = 600)
netVisual_individual(flc.cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord", color.use = cols)
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLC_FGF_L-R_contribution.png", width = 4, height = 3, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("FGF"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/FGF/FLC_diagram_LRpairs_Expression_allProteins.png", width = 7, height = 5, units = "in", res = 600)
plotGeneExpression(flc.cellchat, signaling = "FGF", enriched.only = FALSE, color.use = cols)
dev.off()
```


### VEGFA pathway dissection

```{r}
pathways.show <- c("VEGF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLCchord_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLCchord_L-R_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("VEGF"), legend.pos.x = 8)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PERIO <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PERIO[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLCchord_diagram_LRpair.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLC_PERIOSTIN_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("VEGF"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/VEGF/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "VEGF", enriched.only = TRUE)
dev.off()
```

### TGFb pathway dissection

```{r}
pathways.show <- c("TGFb") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLCchord_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLCchord_L-R_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("TGFb"), legend.pos.x = 8, lab.cex = 1.5)
dev.off()
```


```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PERIO <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PERIO[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLCchord_diagram_LRpair.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLC_PERIOSTIN_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("TGFb"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/TGFb/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "TGFb", enriched.only = TRUE)
dev.off()
```

### CALCR pathway dissection

```{r}
pathways.show <- c("CALCR") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(flc.cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(flc.cellchat, signaling = pathways.show, layout = "circle", color.use = cols)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLCchord_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(flc.cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1, color.use = cols)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLCchord_L-R_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_chord_gene(flc.cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("CALCR"), legend.pos.x = 8, lab.cex = 1.5, color.use = cols)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLC_heatmap.png", width = 5, height = 4.5, units = "in", res = 300)
netVisual_heatmap(flc.cellchat, signaling = pathways.show, color.heatmap = "Reds", color.use = cols)
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.CALCR <- extractEnrichedLR(flc.cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.CALCR[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLCchord_diagram_LRpair.png", width = 7, height = 7, units = "in", res = 600)
netVisual_individual(flc.cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord", color.use = cols)
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLC_CALCR_L-R_contribution.png", width = 4, height = 3, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("CALCR"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/CALCR/FLC_diagram_LRpairs_Expression.png", width = 7, height = 5, units = "in", res = 600)
plotGeneExpression(flc.cellchat, signaling = "CALCR", enriched.only = TRUE, color.use = cols)
dev.off()
```

### EGF analysis

```{r}
pathways.show <- c("EGF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLCchord_diagram.png", width = 10, height = 10, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLCchord_L-R_diagram.png", width = 10, height = 10, units = "in", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("EGF"), legend.pos.x = 8, lab.cex = 1.2)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PERIO <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PERIO[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLCchord_diagram_LRpair.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLC_EGF_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("EGF"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/EGF/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "EGF", enriched.only = TRUE)
dev.off()
```



### SPP1 analysis

```{r}
pathways.show <- c("SPP1") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLCchord_diagram.png", width = 10, height = 10, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLCchord_L-R_diagram.png", width = 10, height = 10, units = "in", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("SPP1"), legend.pos.x = 8, lab.cex = 1.2)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PERIO <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PERIO[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLCchord_diagram_LRpair.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLC_SPP1_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("SPP1"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/SPP1/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "SPP1", enriched.only = TRUE)
dev.off()
```




### MIF analysis

```{r}
pathways.show <- c("MIF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLCchord_diagram.png", width = 10, height = 10, units = "in", res = 600)
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLCchord_L-R_diagram.png", width = 10, height = 10, units = "in", res = 600)
netVisual_chord_gene(cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("MIF"), legend.pos.x = 8, lab.cex = 1.2)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLC_heatmap.png", width = 10, height = 8, units = "in", res = 300)
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.PERIO <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.PERIO[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLCchord_diagram_LRpair.png", width = 10, height = 8, units = "in", res = 600)
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord")
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLC_MIF_L-R_contribution.png", width = 5, height = 4, units = "in", res = 600)
netVisual_bubble(cellchat,remove.isolate = FALSE, signaling = c("MIF"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/MIF/FLC_diagram_LRpairs_Expression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat, signaling = "MIF", enriched.only = TRUE)
dev.off()
```
### GDF analysis

```{r}
pathways.show <- c("GDF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = seq(1,4) # a numeric vector. 
netVisual_aggregate(flc.cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLCcircle_diagram.png", width = 10, height = 8, units = "in", res = 600)
netVisual_aggregate(flc.cellchat, signaling = pathways.show, layout = "circle", color.use = cols)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLCchord_diagram.png", width = 8, height = 8, units = "in", res = 600)
netVisual_aggregate(flc.cellchat, signaling = pathways.show, layout = "chord", vertex.label.cex = 1, color.use = cols)
dev.off()
```

```{r}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLCchord_L-R_diagram.png", width = 8, height = 8, units = "in", res = 600)
netVisual_chord_gene(flc.cellchat, sources.use = c(1:12), targets.use = c(1:12), signaling = c("GDF"), legend.pos.y = 2, legend.pos.x = -5, lab.cex = 1.2, color.use = cols)
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLC_heatmap.png", width = 5, height = 4.5, units = "in", res = 300)
netVisual_heatmap(flc.cellchat, signaling = pathways.show, color.heatmap = "Reds", color.use = cols)
dev.off()
#> Do heatmap based on a single object
```

```{r}
pairLR.GDF <- extractEnrichedLR(flc.cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.GDF[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLCchord_diagram_LRpair.png", width = 7, height = 7, units = "in", res = 600)
netVisual_individual(flc.cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord", color.use = cols)
dev.off()
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLC_GDF_L-R_contribution.png", width = 6.3, height = 4, units = "in", res = 600)
netVisual_bubble(flc.cellchat,remove.isolate = FALSE, signaling = c("GDF"))
dev.off()
#> Comparing communications on a single object
```

```{r Plot gene expression}
png(file ="./revisedDataset/cellChat/FLCnew/plots/pathwayDissections/GDF/FLC_diagram_LRpairs_Expression_allProteins.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(flc.cellchat, signaling = "GDF", enriched.only = FALSE, color.use = cols)
dev.off()
```


### Part IV: Systems analysis of cell-cell communication network

```{r}
dir.create("./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis")
```


```{r}
ptm = Sys.time()
# Compute the network centrality scores
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups
netAnalysis_signalingRole_network(cellchat, signaling = pathways.show, width = 8, height = 2.5, font.size = 10)
```

```{r}
# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
gg1 <- netAnalysis_signalingRole_scatter(cellchat)
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
# Signaling role analysis on the cell-cell communication networks of interest
gg2 <- netAnalysis_signalingRole_scatter(cellchat, signaling = c("PERIOSTIN", "VEGFA", "TGFb", "PDGF", "FGF", "CALCR"))
#> Signaling role analysis on the cell-cell communication network from user's input
gg1 + gg2
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/SignalingRolesScatter.png", width = 5, height = 4, units = "in", res = 600)
gg1
dev.off()
```

```{r}
# Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
ht1 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "outgoing")
ht2 <- netAnalysis_signalingRole_heatmap(cellchat, pattern = "incoming")
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/SignalingRole_out-in-going.png", width = 10, height = 6, units = "in", res = 600)
ht1 + ht2
dev.off()
```
## Identify global communication patterns to explore how multiple cell types and signaling pathways coordinate together

### Identify and visualize outgoing communication pattern of secreting cells

```{r}
selectK(cellchat, pattern = "outgoing")
```

```{r}
nPatterns = 3
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/OutgoingPatterns.png", width = 10, height = 3, units = "in", res = 600)
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)
dev.off()
```

```{r}
# river plot
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/OutgoingPatterns_riverplot.png", width = 10, height = 6, units = "in", res = 600)
netAnalysis_river(cellchat, pattern = "outgoing")
dev.off()
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
# dot plot
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/OutgoingPatterns_dotplot.png", width = 10, height = 6, units = "in", res = 600)
netAnalysis_dot(cellchat, pattern = "outgoing")
dev.off()
```
### Incoming signaling

```{r}
selectK(cellchat, pattern = "incoming")
```

```{r}
nPatterns = 2
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/IncomingPatterns.png", width = 10, height = 3, units = "in", res = 600)
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "incoming", k = nPatterns)
dev.off()
```
```{r}
# river plot
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/IncomingPatterns_riverplot.png", width = 10, height = 6, units = "in", res = 600)
netAnalysis_river(cellchat, pattern = "incoming")
dev.off()
#> Please make sure you have load `library(ggalluvial)` when running this function
```

```{r}
# dot plot
png(file ="./revisedDataset/cellChat/FLCnew/plots/SystemsLevelAnalysis/IncomingPatterns_dotplot.png", width = 10, height = 6, units = "in", res = 600)
netAnalysis_dot(cellchat, pattern = "incoming")
dev.off()
```

### Manifold and classification learning analysis of signaling networks

```{r}
use_python("/home/af547/miniconda3/bin/python")
cellchat <- computeNetSimilarity(cellchat, type = "functional")
cellchat <- netEmbedding(cellchat, type = "functional")
#> Manifold learning of the signaling networks for a single dataset
cellchat <- netClustering(cellchat, type = "functional", do.parallel = FALSE)
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchat, type = "functional", label.size = 3.5)
```

```{r}
cellchat <- computeNetSimilarity(cellchat, type = "structural")
cellchat <- netEmbedding(cellchat, type = "structural")
#> Manifold learning of the signaling networks for a single dataset
cellchat <- netClustering(cellchat, type = "structural", do.parallel = FALSE)
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchat, type = "structural", label.size = 3.5)
```

```{r}
saveRDS(flc.cellchat, "./fullDataset/rds/scRNA_FLCnew-2.rds")
```

