---
title: "10% truncated cellchat analysis"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries}
library(Seurat)
library(tidyverse)
library(CellChat)
library(patchwork)
library(svglite)
library(ggalluvial)
library(NMF)
library(reticulate)
options(stringsAsFactors = FALSE)
```

```{r set seed and project name, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r}
flc.cellchat <- readRDS(file = "./revisedDataset/rds/scRNA_FLCnew-trunc0.15.rds")
nml.cellchat <- readRDS(file = "./revisedDataset/rds/scRNA_NMLnew-trunc0.15.rds")
object.list <- list(NML = nml.cellchat, FLC = flc.cellchat)
cellchat.combined <- readRDS("./revisedDataset/cellChat/merged/FLC_NML_combinedCellchat_trunc0.15.rds")
```

```{r}
levels = c("Liver epithelial cells 1","Liver epithelial cells 2", "Liver epithelial cells 3", "Liver epithelial cells 4", "Liver epithelial cells 5", "Liver epithelial cells 6", "Endothelial cells", "Stellate cells", "Neutrophils and macrophages", "Lymphocytes", "Cholangiocyte cells", "Unknown") # set factor
flc.cellchat <- updateClusterLabels(cellchat.combined, new.order = levels)
```


```{r}
cols <- c("Liver epithelial cells 1" = "#0072B2",
             "Liver epithelial cells 2" = "#cab2d6",
             "Endothelial cells" = "#6a3d9a",
             "Liver epithelial cells 3" = "#DDCC77",
             "Liver epithelial cells 4" = "#ff7f00",
             "Stellate cells" = "#33a02c",
             "Liver epithelial cells 5" = "#AA4499",
             "Cholangiocyte cells" = "#CC6677",
             "Neutrophils and macrophages" = "#44AA99",
             "Lymphocytes" = "#8C87E6",
             "Liver epithelial cells 6" = "#FF6B6B",
             "Unknown" = "#b15928")
```


```{r}
## This is done with the alternative approach to getting counts, which is normalizing the RNA and then separating by tissue status
dir.create("./revisedDataset/cellChat/merged/trunc0.15")
dir.create("./revisedDataset/cellChat/merged/trunc0.15/plots")
```

```{r Combine both cellchat objects}
cellchat.combined <- mergeCellChat(object.list, add.names = names(object.list), merge.data = FALSE)
```

## Part I: Predict general principles of cell-cell communication

```{r}
dir.create("./revisedDataset/cellChat/merged/trunc0.1")
dir.create("./revisedDataset/cellChat/merged/trunc0.1/plots")
```

```{r}
gg1 <- compareInteractions(cellchat.combined, show.legend = F, group = c(1,2), x.lab.rot = TRUE, angle.x = 90, color.use = c("#a6cee3", "#1f78b4"))
gg2 <- compareInteractions(cellchat.combined, show.legend = F, group = c(1,2), measure = "weight", color.use = c("#a6cee3", "#1f78b4"))
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/Number_strength-compareInteractions.png", width = 5, height = 4, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
gg1 <- netVisual_diffInteraction(cellchat.combined, weight.scale = T, color.use = cols)
gg2 <- netVisual_diffInteraction(cellchat.combined, weight.scale = T, measure = "weight", color.use = cols)
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/Number_strength-Circleplot.png", width = 10, height = 4, units = "in", res = 600)
gg1
gg2
dev.off()
```

```{r}
gg1 <- netVisual_heatmap(cellchat.combined, color.use = cols)
#> Do heatmap based on a merged object
gg2 <- netVisual_heatmap(cellchat.combined, measure = "weight", color.use = cols)
#> Do heatmap based on a merged object
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/Number_strength-heatmap.png", width = 8, height = 5, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/Number_byStatus_circlePlot.png", width = 7, height = 4, units = "in", res = 600)
weight.max <- getMaxWeight(object.list, attribute = c("idents","count"))
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_circle(object.list[[i]]@net$count, weight.scale = T, label.edge= F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = paste0("Number of interactions - ", names(object.list)[i]), color.use = cols)
}
dev.off()

png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/Number_byStatus_NML.png", width = 10, height = 10, units = "in", res = 600)
netVisual_circle(object.list$NML@net$count, weight.scale = T, label.edge = F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name =  "Number of interactions - NML", color.use = cols)
dev.off()

netVisual_circle(object.list$FLC@net$count, weight.scale = T, label.edge = F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = "Number of interactions - FLC", color.use = cols)
```


```{r}
num.link <- sapply(object.list, function(x) {rowSums(x@net$count) + colSums(x@net$count)-diag(x@net$count)})
weight.MinMax <- c(min(num.link), max(num.link)) # control the dot size in the different datasets
gg <- list()
for (i in 1:length(object.list)) {
  gg[[i]] <- netAnalysis_signalingRole_scatter(object.list[[i]], title = names(object.list)[i], weight.MinMax = weight.MinMax, color.use = cols)
}
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways

png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/SignalingRoleByStatus_heatmap.png", width = 9, height = 4, units = "in", res = 600)
patchwork::wrap_plots(plots = gg)
dev.off()
```

```{r}
num.link <- sapply(object.list, function(x) {rowSums(x@net$count) + colSums(x@net$count)-diag(x@net$count)})
weight.MinMax <- c(min(num.link), max(num.link)) # control the dot size in the different datasets
gg <- list()
for (i in 1:length(object.list)) {
  gg[[i]] <- netAnalysis_signalingRole_scatter(object.list[[i]], title = names(object.list)[i], weight.MinMax = weight.MinMax, signaling = c("FGF"), color.use = cols)
}
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways
#> Signaling role analysis on the aggregated cell-cell communication network from all signaling pathways

png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/SignalingRole_F_heatmap.png", width = 9, height = 4, units = "in", res = 600)
patchwork::wrap_plots(plots = gg)
dev.off()
```

```{r}
gg1 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Endothelial cells", signaling.label = c("PDGF", "TGFb"), dot.size = 2)
gg2 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Neutrophils and macrophages", signaling.label = "TGFb", dot.size = 2)
gg3 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Stellate cells", signaling.label = c("TGFb"), dot.size = 2, top.label = .6)
png(file ="./revisedDataset/cellChat/merged/plots/SignalingChanges_scatter.png", width = 18, height = 4, units = "in", res = 600)
patchwork::wrap_plots(plots = list(gg1,gg2,gg3))
dev.off()
```

```{r}
gg2 <- netAnalysis_signalingChanges_scatter(cellchat.combined, idents.use = "Stellate cells", signaling = c("FGF", "CALCR"))
```


### Identify signaling groups based on their functional similarity

```{r}
use_python("/home/af547/miniconda3/bin/python")
cellchat.combined <- computeNetSimilarityPairwise(cellchat.combined, type = "functional")
cellchat.combined <- netEmbedding(cellchat.combined, type = "functional")
cellchat.combined <- netClustering(cellchat.combined, type = "functional", do.parallel = FALSE)
netVisual_embeddingPairwise(cellchat.combined, type = "functional", label.size = 3.5)
```

```{r}
cellchat.combined <- computeNetSimilarityPairwise(cellchat.combined, type = "structural")
cellchat.combined <- netEmbedding(cellchat.combined, type = "structural")
cellchat.combined <- netClustering(cellchat.combined, type = "structural", do.parallel = FALSE)
# Visualization in 2D-space
netVisual_embeddingPairwise(cellchat.combined, type = "structural", label.size = 3.5)
netVisual_embeddingPairwiseZoomIn(cellchat.combined, type = "structural", nCol = 2)
```

### Compute and visualize the pathway distance in the learned joint manifold

```{r}
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/RankSimilarity.png", width = 3, height = 3, units = "in", res = 600)
rankSimilarity(cellchat.combined, type = "functional", color.use = c("#a6cee3", "#1f78b4"))
dev.off()
#> Compute the distance of signaling networks between datasets 1 2
```

### Identify and visualize the conserved and context-specific signaling pathways

#### Compare the overall information flow of each signaling pathway

```{r}
gg1 <- rankNet(cellchat.combined, mode = "comparison", stacked = T, do.stat = TRUE, color.use = c("#a6cee3", "#1f78b4"))
gg2 <- rankNet(cellchat.combined, mode = "comparison", stacked = F, do.stat = TRUE, color.use = c("#a6cee3", "#1f78b4"))
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/RankNet.png", width = 7, height = 5, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
library(ComplexHeatmap)
i = 1
pathway.union <- union(object.list[[i]]@netP$pathways, object.list[[i+1]]@netP$pathways)
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6, color.use = cols)
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 6, color.use = cols)
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/OutgoingSignalingRole_heatmap.png", width = 8, height = 6, units = "in", res = 600)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6, color.heatmap = "GnBu", color.use = cols)
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 6, color.heatmap = "GnBu", color.use = cols)
png(file = "./revisedDataset/cellChat/merged/trunc0.15/plots/IncomingSignalingRole_heatmap.png", width = 8, height = 6, units = "in", res = 600)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "all", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6, color.heatmap = "OrRd", color.use = cols)
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i+1]], pattern = "all", signaling = pathway.union, title = names(object.list)[i+1], width = 5, height = 6, color.heatmap = "OrRd", color.use = cols)
png(file ="./revisedDataset/cellChat/merged/plots/AllSignalingRole_heatmap.png", width = 8, height = 6, units = "in", res = 600)
draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))
dev.off()
```

### Part III: Identify the upgulated and down-regulated signaling ligand-receptor pairs 

```{r}
netVisual_bubble(cellchat.combined, signaling = "PDGF", comparison = c(1, 2), angle.x = 45)
#> Comparing communications on a merged object
```
```{r}
gg1 <- netVisual_bubble(cellchat.combined, sources.use = 4, targets.use = c(5:11),  comparison = c(1, 2), max.dataset = 2, title.name = "Increased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg2 <- netVisual_bubble(cellchat.combined, sources.use = 4, targets.use = c(5:11),  comparison = c(1, 2), max.dataset = 1, title.name = "Decreased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg1 + gg2
```


#### Identify dysfunctional signaling by using differential expression analysis

```{r}
pos.dataset = "FLC"
features.name = paste0(pos.dataset, ".merged")
```

```{r}
cellchat.combined <- identifyOverExpressedGenes(cellchat.combined, group.dataset = "datasets", pos.dataset = pos.dataset, features.name = features.name, only.pos = FALSE, thresh.pc = 0.1, thresh.fc = 0.05,thresh.p = 0.05) 
```

```{r}
net <- netMappingDEG(cellchat.combined, features.name = features.name)
net.up <- subsetCommunication(cellchat.combined, net = net, datasets = "FLC",ligand.logFC = 0.05, receptor.logFC = NULL)
net.down <- subsetCommunication(cellchat.combined, net = net, datasets = "NML",ligand.logFC = -0.05, receptor.logFC = NULL)
```

```{r}
gene.up <- extractGeneSubsetFromPair(net.up, cellchat.combined)
gene.down <- extractGeneSubsetFromPair(net.down, cellchat.combined)
```

```{r}
pairLR.use.up = net.up[, "interaction_name", drop = F]
gg1 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.up, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
gg2 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.down, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object

png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/Upregulated-downregulated_dotplot.png", width = 10, height = 6, units = "in", res = 600)
gg1 + gg2
dev.off()
```


### Identify the upgulated (increased) and down-regulated (decreased) signaling ligand-receptor pairs 

```{r PDGF l-r pairs}
gg1 <- netVisual_bubble(cellchat.combined, signaling = "PDGF", max.dataset = 2, title.name = "Increased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg2 <- netVisual_bubble(cellchat.combined, signaling = "PDGF", max.dataset = 1, title.name = "Decreased signaling in LS", angle.x = 45, remove.isolate = T)
#> Comparing communications on a merged object
gg1 + gg2
```


```{r}
pathways.show <- c("PERIOSTIN") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

### Visually compare cell to cell communication

```{r}
pathways.show <- c("FGF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

```{r}
pathways.show <- c("FGF") 
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
```

### Part IV: Visually compare cell-cell communication using Hierarchy plot, Circle plot or Chord diagram

#### MIF

```{r}
dir.create("./revisedDataset/cellChat/merged/trunc0.15/plots/MIF")
```

```{r}
pathways.show <- c("MIF") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]), color.use = cols)
}
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]), color.use = cols)
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIF_heatmap.png", width = 8, height = 4.5, units = "in", res = 600)
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
pairLR.MIF <- extractEnrichedLR(flc.cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.MIF[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFchord_diagram_CXCR4.png", width = 8, height = 8, units = "in", res = 600)
netVisual_individual(flc.cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord", color.use = cols)
dev.off()
```

```{r}
# Chord diagram
pathways.show <- c("MIF") 
pairLR.MIF <- extractEnrichedLR(cellchat.combined, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.MIF[2,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFchord_diagram_LRpair2.png", width = 7, height = 7, units = "in", res = 600)
for (i in 1:length(object.list)) {
  netVisual_individual(object.list[[i]], signaling = pathways.show, pairLR.use = LR.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]))
}
dev.off()
```
```{r}
cellchat.combined@meta$datasets = factor(cellchat.combined@meta$datasets, levels = c("NML", "FLC")) # set factor level
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIF_splitGeneExpression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat.combined, signaling = "MIF", split.by = "datasets", colors.ggplot = T)
dev.off()
```

```{r}
pairLR.use.up = net.up[, "interaction_name", drop = F]
gg1 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.up, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
gg2 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.down, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object

png(file ="./revisedDataset/cellChat/merged/plots/Upregulated-downregulated_dotplot.png", width = 10, height = 6, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
b <- netVisual_bubble(cellchat.combined, signaling = "MIF", comparison = c(1, 2), return.data = FALSE, angle.x = 45)
```

```{r}
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFcombined_dotplot.png", width = 11.5, height = 5.2, units = "in", res = 600)
netVisual_bubble(cellchat.combined, signaling = "MIF", comparison = c(1, 2), return.data = FALSE, angle.x = 45, color.text = c("#6baed6", "#2171b5")) +
    theme(plot.margin = unit(c(1,1,1,1), "in"))
dev.off()
```

```{r}
pairLR.MIF <- extractEnrichedLR(cellchat.combined, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.MIF[2,] # show one ligand-receptor pair
for (i in 1:length(object.list)) {
png(file = paste0("./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFchord_", i, "_diagram_LRpair1.png"), width = 7, height = 7, units = "in", res = 600)
  netVisual_individual(object.list[[i]], signaling = pathways.show, pairLR.use = LR.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]), color.use = cols)
}
dev.off()
```

#### CXCL

```{r}
dir.create("./revisedDataset/cellChat/merged/trunc0.15/plots/CXCL")
```

```{r}
pathways.show <- c("CXCL") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]), color.use = cols)
}
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]), color.use = cols)
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIF_heatmap.png", width = 8, height = 4.5, units = "in", res = 600)
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
dev.off()
```

```{r}
pairLR.MIF <- extractEnrichedLR(flc.cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.MIF[1,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFchord_diagram_CXCR4.png", width = 8, height = 8, units = "in", res = 600)
netVisual_individual(flc.cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "chord", color.use = cols)
dev.off()
```

```{r}
# Chord diagram
pathways.show <- c("MIF") 
pairLR.MIF <- extractEnrichedLR(cellchat.combined, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.MIF[2,] # show one ligand-receptor pair
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFchord_diagram_LRpair2.png", width = 7, height = 7, units = "in", res = 600)
for (i in 1:length(object.list)) {
  netVisual_individual(object.list[[i]], signaling = pathways.show, pairLR.use = LR.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]))
}
dev.off()
```
```{r}
cellchat.combined@meta$datasets = factor(cellchat.combined@meta$datasets, levels = c("NML", "FLC")) # set factor level
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIF_splitGeneExpression.png", width = 8, height = 6, units = "in", res = 600)
plotGeneExpression(cellchat.combined, signaling = "MIF", split.by = "datasets", colors.ggplot = T)
dev.off()
```

```{r}
pairLR.use.up = net.up[, "interaction_name", drop = F]
gg1 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.up, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Up-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object
pairLR.use.down = net.down[, "interaction_name", drop = F]
gg2 <- netVisual_bubble(cellchat.combined, pairLR.use = pairLR.use.down, sources.use = 4, targets.use = c(5:11), comparison = c(1, 2),  angle.x = 90, remove.isolate = T,title.name = paste0("Down-regulated signaling in ", names(object.list)[2]))
#> Comparing communications on a merged object

png(file ="./revisedDataset/cellChat/merged/plots/Upregulated-downregulated_dotplot.png", width = 10, height = 6, units = "in", res = 600)
gg1 + gg2
dev.off()
```

```{r}
b <- netVisual_bubble(cellchat.combined, signaling = "MIF", comparison = c(1, 2), return.data = FALSE, angle.x = 45)
```

```{r}
png(file ="./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFcombined_dotplot.png", width = 11.5, height = 5.2, units = "in", res = 600)
netVisual_bubble(cellchat.combined, signaling = "MIF", comparison = c(1, 2), return.data = FALSE, angle.x = 45, color.text = c("#6baed6", "#2171b5")) +
    theme(plot.margin = unit(c(1,1,1,1), "in"))
dev.off()
```

```{r}
pairLR.MIF <- extractEnrichedLR(cellchat.combined, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.MIF[2,] # show one ligand-receptor pair
for (i in 1:length(object.list)) {
png(file = paste0("./revisedDataset/cellChat/merged/trunc0.15/plots/MIF/MIFchord_", i, "_diagram_LRpair1.png"), width = 7, height = 7, units = "in", res = 600)
  netVisual_individual(object.list[[i]], signaling = pathways.show, pairLR.use = LR.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]), color.use = cols)
}
dev.off()
```
