---
title: "Differential expression"
output: html_document
date: "2023-07-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-libraries}
library(Seurat)
library(tidyverse)
```

# Single cell RNAseq analysis

This is the continued single nuclei RNAseq analysis of FLC provided by the Khasayer lab.

## Seurat analysis

### Find markers

```{r find-markers, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r}
harmonized.seurat <- readRDS('./fullDataset/rds/FLCvNML_harmonized-byID-obj.rds')
```

```{r}
levels(harmonized.seurat)
```

## Differential expression within assigned cluster

For the differential expression, we can use FindMarkers or FindConservedMarkers. Since we have 2 samples (1 WT and 1 KO), we will use FindMarkers. If we had two separate sequencing sets with potentially large batch effects, we could use FindConservedMarkers instead.

```{r}
harmonized.seurat <- PrepSCTFindMarkers(harmonized.seurat)
```


```{r find-differentially-expressed, warning=F}
# For each cluster
DefaultAssay(harmonized.seurat) <- "RNA"
deg <- data.frame()
for (c in levels(Idents(harmonized.seurat))) {
  print(paste0("Generating differential expression within cluster: ", c))
  sub_obj <- subset(harmonized.seurat, idents = c)
  print(levels(Idents(sub_obj)))
  Idents(sub_obj) <- "status"
  print(levels(Idents(sub_obj)))
  print(sub_obj)
  
  mks <- FindMarkers(sub_obj, 
                     ident.1 = "FLC", 
                     ident.2 = "NML", 
                     test.use = "MAST", 
                     min.pct = -Inf, 
                     logfc.threshold = -Inf,
                     assay = "RNA",
                     latent.vars = c('percent.mt', 'nFeature_RNA'))
  
  exp <- AverageExpression(sub_obj, assays = "RNA")$RNA %>%
    as.data.frame() %>%
    rownames_to_column(var = "gene")
  
  names(exp)[2:3] <- paste0("exp_", names(exp)[2:3])
  
  mks <- mks %>% 
    as.data.frame() %>%
    mutate(gene = row.names(.),
           cluster = c) %>%
    left_join(exp)
  deg <- bind_rows(deg, mks)
  print(head(deg))
}

head(deg)

write_csv(deg, file = paste0("./revisedDataset/", proj_name, '_DEG_clusterNamed_FLCvsNML-MAST.csv'))
```


## Session info

```{r session-info}

sessionInfo()

```