---
title: "Cell chat analysis"
output: html_document
date: "2023-07-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries}
library(Seurat)
library(tidyverse)
library(CellChat)
library(patchwork)
library(svglite)
library(ggalluvial)
library(NMF)
options(stringsAsFactors = FALSE)
```

```{r set seed and project name, warning=F, message=F}
set.seed(1234)
proj_name <- "FLCvNML"
```

```{r load objects}
harmonized.seurat <- readRDS('./revisedDataset/rds/FLCvNML_Named-obj.rds')
DefaultAssay(harmonized.seurat) <- "SCT"
cellchat <-  readRDS("./revisedDataset/rds/scRNA_cellchat_FLC_final.rds")
```

```{r}
labels <- Idents(harmonized.seurat)
meta <- data.frame(group = labels, row.names = names(labels))
```

```{r Create a CellChat object}
cellchat <- createCellChat(object = harmonized.seurat)
```

```{r Add cell information into meta slot of the object}
cellchat <- addMeta(cellchat, meta = meta, meta.name = "group")
cellchat <- setIdent(cellchat, ident.use = "group") # set "labels" as default cell identity
levels(cellchat@idents) # show factor levels of the cell labels
groupSize <- as.numeric(table(cellchat@idents))
```

```{r Set the ligand-receptor interaction database}
CellChatDB <- CellChatDB.human # use CellChatDB.mouse if running on mouse data
showDatabaseCategory(CellChatDB)
```

```{r}
dplyr::glimpse(CellChatDB$interaction)
CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling") # use Secreted Signaling
cellchat@DB <- CellChatDB.use
```

```{r Preprocessing the expression data for cell-cell communication analysis}
# subset the expression data of signaling genes for saving computation cost
cellchat <- subsetData(cellchat) # This step is necessary even if using the whole database
future::plan("multisession", workers = 85) # do parallel
cellchat <- identifyOverExpressedGenes(cellchat)
cellchat <- identifyOverExpressedInteractions(cellchat)
cellchat <- projectData(cellchat, PPI.human)
saveRDS(cellchat, "./revisedDataset/rds/scRNA_revised_cellchat.rds")
cellchat <- readRDS("./revisedDataset/rds/scRNA_revised_cellchat.rds")
```

```{r}
cellchat <- computeCommunProb(cellchat)
saveRDS(cellchat, "./revisedDataset/rds/scRNA_cellchat2.rds")
# Load cellchat data
cellchat <- readRDS(file = "./revisedDataset/rds/scRNA_cellchat2.rds")
#> triMean is used for calculating the average gene expression per cell group. 
#> [1] ">>> Run CellChat on sc/snRNA-seq data <<< [2022-11-26 08:34:38]"
#> [1] ">>> CellChat inference is done. Parameter values are stored in `object@options$parameter` <<< [2022-11-26 08:35:36]"
# Filter out the cell-cell communication if there are only few number of cells in certain cell groups
cellchat <- filterCommunication(cellchat, min.cells = 10)
```

```{r Infer the cell-cell communication at a signaling pathway level}
cellchat <- computeCommunProbPathway(cellchat)
```

```{r Calculate the aggregated cell-cell communication network}
dir.create("./revisedDataset/cellChat")
cellchat <- aggregateNet(cellchat)
groupSize <- as.numeric(table(cellchat@idents)) # number of cells in each cell group
levels(cellchat@idents)
```

```{r Subset the inferred cell-cell communications of interest}
df.net <- subsetCommunication(cellchat)

df_net <- subsetCommunication(cellchat, signaling = c(unique(df.net$pathway_name)), slot.name = "net")
df_net
write.csv(df.net, "./revisedDataset/cellChat/cellChat-allInferredCommunications.csv")
write.csv(df_net, "./revisedDataset/cellChat/cellChat-upregulatedPathways-ofInterest.csv")
```

## Calculate the aggregated cell-cell communication network
```{r}
dir.create("./revisedDataset/cellChat/plots")
groupSize <- as.numeric(table(cellchat@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions", shape = "circle", vertex.label.cex = .8, margin = .5)
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength", vertex.label.cex = .8, margin = .5)
```

```{r}
png("./revisedDataset/cellChat/plots/aggregatedCommunicationNetwork_NumberofInteractions_count.png", width = 6, height = 6, units = "in", res = 300)  # Adjust dimensions and resolution
netVisual_circle(cellchat@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions", shape = "circle", vertex.label.cex = .8, margin = .5)
dev.off()
```

```{r}
png("./revisedDataset/cellChat/plots/aggregatedCommunicationNetwork_NumberofInteractions_weight.png", width = 6, height = 6, units = "in", res = 300)  # Adjust dimensions and resolution
netVisual_circle(cellchat@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength", vertex.label.cex = .8, margin = .5)
dev.off()
```


```{r}
mat <- cellchat@net$weight
par(mfrow = c(3,4), xpd=TRUE)
for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
}
```

```{r}
# Iterate through each row in mat
for (i in 1:nrow(mat)) {
  # Create a new matrix with zeros and set the current row values
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  
  # Define the output file name
  output_filename <- paste0("./revisedDataset/cellChat/plots/", "aggregatedCommunicationNetwork_byCell_weight", i, ".png")
  
  # Open a new graphics device and save the plot
  png(output_filename, width = 6, height = 6, units = "in", res = 300)
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = TRUE, edge.weight.max = max(mat), title.name = rownames(mat)[i])
  dev.off()
}
```

## Part III: Visualization of cell-cell communication network

```{r }
# pathways showing significant communications
cellchat@netP$pathways
```

```{r}
pathways.show <- c("VEGF") 
# Hierarchy plot
# Here we define `vertex.receive` so that the left portion of the hierarchy plot shows signaling to fibroblast and the right portion shows signaling to immune cells 
vertex.receiver = c(1) # a numeric vector. 
netVisual_aggregate(cellchat, signaling = pathways.show,  vertex.receiver = vertex.receiver)
# Circle plot
par(mfrow=c(1,1))
```

```{r}
png("./revisedDataset/cellChat/plots/aggregatedCommunicationNetwork_VEGF.png", width = 6, height = 6, units = "in", res = 300)  # Adjust dimensions and resolution
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "circle")
dev.off()
```

```{r}
par(mfrow=c(1,1))
png("./revisedDataset/cellChat/plots/aggregatedCommunicationNetwork_VEGF_chord.png", width = 6, height = 6, units = "in", res = 300)  # Adjust dimensions and resolution
netVisual_aggregate(cellchat, signaling = pathways.show, layout = "chord")
dev.off()
```

```{r}
# Heatmap
par(mfrow=c(1,1))
netVisual_heatmap(cellchat, signaling = pathways.show, color.heatmap = "Reds")
#> Do heatmap based on a single object
```

```{r}
for (i in pathways.show.all) {
  dir.create(paste0("./revisedDataset/cellChat/", i))
  }
```

### Automatically save the plots of the all inferred network for quick exploration
```{r}
# Access all the signaling pathways showing significant communications
pathways.show.all <- cellchat@netP$pathways
# check the order of cell identity to set suitable vertex.receiver
levels(cellchat@idents)
vertex.receiver = seq(3)
for (i in 1:length(pathways.show.all)) {
  # Visualize communication network associated with both signaling pathway and individual L-R pairs
  netVisual(cellchat, signaling = pathways.show.all[i], vertex.receiver = vertex.receiver, layout = "hierarchy")
  # Compute and visualize the contribution of each ligand-receptor pair to the overall signaling pathway
  gg <- netAnalysis_contribution(cellchat, signaling = pathways.show.all[i])
  ggsave(filename=paste0("./revisedDataset/cellChat/", pathways.show.all[i], "_L-R_contribution.pdf"), plot=gg, width = 3, height = 2, units = 'in', dpi = 300)
}
```
### Visualize cell-cell communication mediated by a single ligand-receptor pair

We can also visualize the cell-cell communication mediated by a single ligand-receptor pair. We provide a function extractEnrichedLR to extract all the significant interactions (L-R pairs) and related signaling genes for a given signaling pathway.

```{r}
pairLR.VEGFA <- extractEnrichedLR(cellchat, signaling = pathways.show, geneLR.return = FALSE)
LR.show <- pairLR.VEGFA[1,] # show one ligand-receptor pair
# Hierarchy plot
vertex.receiver = seq(1,4) # a numeric vector
netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver)
#> [[1]]
# Circle plot
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")
```

```{r}
LR.show <- pairLR.VEGFA[2,] # show one ligand-receptor pair
# Hierarchy plot
vertex.receiver = seq(1,4) # a numeric vector
netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver)
#> [[1]]
# Circle plot
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")
```

```{r}
LR.show <- pairLR.VEGFA[3,] # show one ligand-receptor pair
# Hierarchy plot
vertex.receiver = seq(1,4) # a numeric vector
netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver)
#> [[1]]
# Circle plot
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")
```

```{r}
LR.show <- pairLR.VEGFA[4,] # show one ligand-receptor pair
# Hierarchy plot
vertex.receiver = seq(1,4) # a numeric vector
netVisual_individual(cellchat, signaling = pathways.show,  pairLR.use = LR.show, vertex.receiver = vertex.receiver)
#> [[1]]
# Circle plot
netVisual_individual(cellchat, signaling = pathways.show, pairLR.use = LR.show, layout = "circle")
```

### Visualize cell-cell communication mediated by multiple ligand-receptors or signaling pathways

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
netVisual_bubble(cellchat, sources.use = 4, targets.use = c(5:11), remove.isolate = FALSE)
#> Comparing communications on a single object
```

```{r}
# show all the significant interactions (L-R pairs) associated with certain signaling pathways
netVisual_bubble(cellchat, sources.use = c(1:12), targets.use = c(3), signaling = c("VEGF"), remove.isolate = FALSE)
#> Comparing communications on a single object
```

```{r}
# show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
netVisual_chord_gene(cellchat, sources.use = c(1), targets.use = c(1:7, 11), lab.cex = 0.5,legend.pos.y = 30)
```

```{r}
# show all the interactions received by Inflam.DC
netVisual_chord_gene(cellchat, sources.use = c(1,2,4,5, 7,11), targets.use = c(3) , legend.pos.x = 15)
```
```{r}
plotGeneExpression(cellchat, signaling = "VEGF")
```

## Part IV: Systems analysis of cell-cell communication network

```{r}
# Compute the network centrality scores
cellchat <- netAnalysis_computeCentrality(cellchat, slot.name = "netP") # the slot 'netP' means the inferred intercellular communication network of signaling pathways
# Visualize the computed centrality scores using heatmap, allowing ready identification of major signaling roles of cell groups
netAnalysis_signalingRole_network(cellchat, signaling = pathways.show, width = 8, height = 2.5, font.size = 10)
```

## Identify global communication patterns to explore how multiple cell types and signaling pathways coordinate together

```{r}
selectK(cellchat, pattern = "outgoing")
nPatterns = 3
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "outgoing", k = nPatterns)
```

```{r}
netAnalysis_river(cellchat, pattern = "outgoing")
```

```{r}
netAnalysis_dot(cellchat, pattern = "outgoing")
```

## Identify and visualize incoming communication pattern of target cells

```{r}
selectK(cellchat, pattern = "incoming")
```

```{r}
nPatterns = 3
cellchat <- identifyCommunicationPatterns(cellchat, pattern = "incoming", k = nPatterns)
```

```{r}
# river plot
netAnalysis_river(cellchat, pattern = "incoming")
#> Please make sure you have load `library(ggalluvial)` when running this function
```
```{r}
# dot plot
netAnalysis_dot(cellchat, pattern = "incoming")
```
## Identify signaling groups based on their functional similarity



```{r}
library(reticulate)
use_python("/home/af547/miniconda3/bin/python")
```


```{r}
cellchat <- computeNetSimilarity(cellchat, type = "functional")
cellchat <- netEmbedding(cellchat, type = "functional")
#> Manifold learning of the signaling networks for a single dataset
cellchat <- netClustering(cellchat, type = "functional", do.parallel=FALSE)
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchat, type = "functional", label.size = 3.5)
```

```{r}
netVisual_embeddingZoomIn(cellchat, type = "functional", nCol = 2)
```

## Identify signaling groups based on structure similarity

```{r}
cellchat <- computeNetSimilarity(cellchat, type = "structural")
cellchat <- netEmbedding(cellchat, type = "structural")
#> Manifold learning of the signaling networks for a single dataset
cellchat <- netClustering(cellchat, type = "structural")
#> Classification learning of the signaling networks for a single dataset
# Visualization in 2D-space
netVisual_embedding(cellchat, type = "structural", label.size = 3.5)
```


```{r}
netVisual_embeddingZoomIn(cellchat, type = "structural", nCol = 4)
```

```{r}
DefaultAssay(harmonized.seurat) <- "SCT"
for (gene in c("C5", "C5AR1")) {
  FeaturePlot(harmonized.seurat, features = gene, pt.size = 0.2, split.by = "status", ncol = 4, label = TRUE)
  ggsave(paste0("./revisedDataset/cellChat/COMPLEMENT/", proj_name, "_", gene, "-featurePlot-integrated-byStatus-SCT-named.png"), units = "in", width = 18, height = 10, dpi = 300)
}
plotGeneExpression(cellchat, signaling = "COMPLEMENT")
```

```{r}
DefaultAssay(harmonized.seurat) <- "SCT"
for (gene in c("PROS1", "AXL")) {
  FeaturePlot(harmonized.seurat, features = gene, pt.size = 0.2, split.by = "status", ncol = 4, label = TRUE)
  ggsave(paste0("./revisedDataset/cellChat/PROS/", proj_name, "_", gene, "-featurePlot-integrated-byStatus-SCT-named.png"), units = "in", width = 18, height = 10, dpi = 300)
}
plotGeneExpression(cellchat, signaling = "PROS")
```

```{r}
DefaultAssay(harmonized.seurat) <- "SCT"
for (gene in c("VEGFA", "VEGFC","FLT1", "KDR", "FLT4")) {
  FeaturePlot(harmonized.seurat, features = gene, pt.size = 0.2, split.by = "status", ncol = 4, label = TRUE)
  ggsave(paste0("./revisedDataset/cellChat/VEGF/", proj_name, "_", gene, "-featurePlot-integrated-byStatus-SCT-named.png"), units = "in", width = 18, height = 10, dpi = 300)
}
plotGeneExpression(cellchat, signaling = "VEGF")
```

```{r}
DefaultAssay(harmonized.seurat) <- "SCT"
for (gene in c("PDGFC", "PDGFRA", "PDGFD", "PDGFRB")) {
  FeaturePlot(harmonized.seurat, features = gene, pt.size = 0.2, split.by = "status", ncol = 4, label = TRUE)
  ggsave(paste0("./revisedDataset/cellChat/PDGF/", proj_name, "_", gene, "-featurePlot-integrated-byStatus-SCT-named.png"), units = "in", width = 18, height = 10, dpi = 300)
}
```


```{r}
saveRDS(cellchat, file = "./revisedDataset/rds/scRNA_cellchat_FLC_final.rds")
```

